### 2019-10-08 paper/article.tex
Initial commit

\documentclass[conference,onecolumn]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-10-08 sorting/gen.py

@@ -1,0 +1,15 @@
+from random import *
+
+n = 50
+eps = 1.0/n
+maxr = n/2
+
+f = open("data.in","w")
+f.write(str(eps) + " " + str(n))
+
+for i in range(n):
+    f.write(" " + str(randint(1,maxr)))
+f.write("\n")
+
+f.close()
+

### 2019-10-10 sorting/gen.py
modificado o gen.py e gerados os dados com 100, 1000 e 10000 numeros aleatorios

@@ -1,15 +1,32 @@
 from random import *
 
-n = 50
-eps = 1.0/n
-maxr = n/2
+n_sizes = [100, 1000, 10000]
+#n_sizes = [1, 2, 3]
 
-f = open("data.in","w")
-f.write(str(eps) + " " + str(n))
+for n in n_sizes:
+    eps = 1.0/n
+    maxr = n/2
+    arq = "_data-%s.in"%(n)
+    f = open(arq,"w")
+    f.write(str(eps) + " " + str(n))
+    for i in range(n):
+        f.write(" " + str(randint(1,maxr)))
+    f.write("\n")
+    f.close()
 
-for i in range(n):
-    f.write(" " + str(randint(1,maxr)))
-f.write("\n")
+# ============================
+# CODIGO ANTERIOR
+# ============================
+# n = 10000
+# eps = 1.0/n
+# maxr = n/2
 
-f.close()
+# f = open("data2.in","w")
+# f.write(str(eps) + " " + str(n))
+
+# for i in range(n):
+#     f.write(" " + str(randint(1,maxr)))
+# f.write("\n")
+
+# f.close()
 

### 2019-10-11 paper/article.tex
poucas mudanças no cabeçalho. Tempo investido na configuração da VPN (o que, no final das contas, é fácil).

@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\author{\IEEEauthorblockN{Alexandro Vladno}
+\IEEEauthorblockA{\textit{Centre for Informatics and Systems} \\
+\textit{University of Coimbra}\\
+Coimbra, Portugal \\
+alexandro.vladno@gmail.com}
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{Fabiano Papaiz}
+\IEEEauthorblockA{\textit{Centre for Informatics and Systems} \\
+\textit{University of Coimbra}\\
+Coimbra, Portugal \\
+fabianopapaiz@gmail.com}
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
+\IEEEauthorblockN{Leo Moreira Silva}
+\IEEEauthorblockA{\textit{Centre of Informatics and Systems} \\
+\textit{University of Coimbra}\\
+Coimbra, Portugal \\
+leo.moreira@me.com}
 }
@@
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
+% \begin{figure}[htbp]
+% \centerline{\includegraphics{fig1.png}}
+% \caption{Example of a figure caption.}
+% \label{fig}
+% \end{figure}
 

### 2019-10-14 paper/Background.tex
inicio da escrita do artigo

\section{Background}

In this section, we'll provide some definitions of memory faults and used sorting algorithms.

\subsection{Memory Faults}

Despite the title of this subsection, when the entire digital system (or software) is considered, there are three terms for computing fault and they have different meanings: failure, fault and error.

A failure denotes an element's inability to perform its functions because of error in the element itself or its environment. A fault is an anomalous physical condition. Causes include design errors, manufacturing problems, damage, fatigue, or other deterioration. Faults resulting from design errors and external factors are especially difficult to model and protect against because their occurrences and effects are hard to predict. An error is a manifestation of a fault in a system, in which the logical state of an element differs from its intended value. A fault in a system does not necessarily result in an error. An error occurs for a particular system state and input when an incorrect next state and/or output results \cite{Nelson1990}.

### 2019-10-14 paper/Introduction.tex
inicio da escrita do artigo

\section{Introduction}
Technology is deeply introduced in people's quotidian supporting a massive number of tasks, for example: searching for a shared car, surfing on the web, sending a message to someone, automating the company's production or using the company's software. Nevertheless, most people don't know that devices are continually dealing with memory failures, faults and errors. These devices were made with large and inexpensive memories, which are also error-prone \cite{Finocchi2004}.

Software behavior may be affected by the problems mentioned before, especially those from memory. We have a memory fault when the correct value that should be stored in a memory location gets altered because of a soft failure. In particular, the content of a location can change unexpectedly, i.e., faults may happen at any time: real memory faults are indeed highly dynamic and unpredictable \cite{Hamdioui2003}.

In the beginning steps of software development, the designer has a general idea of the structure and functions. For each one of these, some algorithms will be produced or used. In the following stages, the outcome software (and its algorithms) will be tested and, then, delivered to the user. Different kinds of algorithms could be written or used in the software, and one of these is the sorting algorithms.

In this paper, we present a discussion about how these sorting algorithms, particularly Quicksort, Mergesort, Insertion Sort and Bubblesort, are affected by memory faults.

### 2019-10-14 paper/article.tex
inicio da escrita do artigo

@@
 \usepackage{xcolor}
+\usepackage{setspace}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
-\end{abstract}
+\input{Abstract}
 
-\begin{IEEEkeywords}
-component, formatting, style, styling, insert
-\end{IEEEkeywords}
+\onehalfspacing
 
-\section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+\input{Introduction}
 
-\section{Ease of Use}
-
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\input{Background}
 
@@
 
-\begin{thebibliography}{00}
-\bibitem{b1} G.
+% \begin{thebibliography}{00}
+% \bibitem{b1} G.
 Eason, B.
@@
 529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
+% \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+% \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+% \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+% \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+% \bibitem{b6} Y.
 Yorozu, M.
@@
 301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
+% \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+% \end{thebibliography}
+
+\bibliography{RM1_Assignment}
+\bibliographystyle{plain}
+
 \vspace{12pt}

### 2019-10-14 paper/MemoryFaults.tex
continuação da escrita do documento

\section{Memory Faults}

Despite the title of this subsection, when the entire digital system (or software) is considered, there are three terms for computing fault and they have different meanings: failure, fault and error \cite{Nelson1990}.

\begin{itemize}
    \item \textit{Failure}: A failure denotes an element's inability to perform its functions because of error in the element itself or its environment, which in turn are caused by various faults;
    \item \textit{Fault}: A fault is an anomalous physical condition. Causes include design errors, manufacturing problems, damage, fatigue, or other deterioration. Faults resulting from design errors and external factors are especially difficult to model and protect against because their occurrences and effects are hard to predict. An error is a manifestation of a fault in a system, in which the logical state of an element differs from its intended value. A fault in a system does not necessarily result in an error;
    \item \textit{Error}: An error is a manifestation of a fault in a system, in which the logical state of an element differs from its intended value. An error occurs for a particular system state and input when an incorrect next state and/or output results.
\end{itemize}

### 2019-10-14 paper/SortingAlgorithms.tex
continuação da escrita do documento

\section{Sorting Algorithms}

This work uses four sorting algorithms: quicksort, mergesort, insertionsort, and bubblesort. In the following subsections, we'll give an overview of them.

\subsection{Quicksort}

Quicksort is an algorithm whose execution time is $\theta(n^2)$ in the worst case over \textit{n} numbers as input. Despite that execution time, quicksort is often the best option for sorting because of its remarkable average efficiency: $\theta(n lg n)$ \cite{Cormen2009}.

\subsection{Mergesort}

\subsection{Insertionsort}

\subsection{Bubblesort}

### 2019-10-21 paper/SortingAlgorithms.tex
continuação da escrita do background

@@
 
-Quicksort is an algorithm whose execution time is $\theta(n^2)$ in the worst case over \textit{n} numbers as input.
+Sorting algorithms are widely used in many aspects of data processing, information searches, business finance, computer encryption, etc.
+Quicksort algorithm, created by Hoare \cite{Hoare1962}, is considered as one of the fastest and best sorting algorithms \cite{Wang2011}.
+The algorithm is based on the paradigm of divide and conquer.
+
+This algorithm has an execution time is $\theta(n^2)$ in the worst case over \textit{n} numbers as input.
 Despite that execution time, quicksort is often the best option for sorting because of its remarkable average efficiency: $\theta(n lg n)$ \cite{Cormen2009}.
 
+The basic steps of this algorithm are \cite{Wang2011}:
+\begin{itemize}
+    \item Pick an element, which is called a pivot, from the list waiting to be sorted;
+    \item Perform partition operation to realize that all elements in the list with values smaller than the pivot came before the pivot.
+Otherwise, all elements in the list with values bigger than the pivot come after it (elements which are equal to pivot can go either way).
+After this partition, the pivot is in the final position of the list;
+    \item Recursively sort the sub-list of smaller elements and the sub-list of the bigger elements.
+\end{itemize}
+
 \subsection{Mergesort}
+
+Mergesort was invented by John Von Newman and is one of the most elegant algorithms to appear in the sorting literature.
+It is the first sorting algorithm to have $\theta(n lg n)$ time complexity bound.
+It is important to observe that this algorithm spends a lot of time on data transfer operations.
+In fact, standard Mergesort incurs about 2n data move operations \cite{Abhyankar2011}.
+
+Conceptually, Mergesort works as follows \cite{Abhyankar2011}:
+\begin{itemize}
+    \item Divide the unsorted array into two sub arrays of about half the size;
+    \item Sort each sub array recursively;
+    \item Merge the two sub arrays back into one array.
+\end{itemize}
 

### 2019-10-21 paper/Abstract.tex
continuação da escrita do background

\begin{abstract}
Although most people in the world use technology devices for many tasks, they don't know how the devices work and how they deal with faults. When those faults occur in memory, software behavior could be affected. Together with the software-specific algorithms are the sorting algorithms used to solve problems like ordering a list of products by their price. This work presents a discussion about how quicksort, mergesort, insertionsort and bubblesort algorithms are affected by memory faults.
\end{abstract}

\begin{IEEEkeywords}
sorting algorithms, memory faults.
\end{IEEEkeywords}

### 2019-10-21 paper/Introduction.tex
continuação da escrita do background

@@
 
+A good algorithm is that which gives satisfactory results for every range of data set.
+Sorting is a fundamental concept and important for solving other problems like is prerequisite for Binary Search.
+Sorting is often used in a large variety of critical applications and is a fundamental task that is used by most computers \cite{NitinArora}.
+
 In this paper, we present a discussion about how these sorting algorithms, particularly Quicksort, Mergesort, Insertion Sort and Bubblesort, are affected by memory faults.

### 2019-10-21 paper/SortingAlgorithms.tex
continuação da escrita do background

@@
 
-This work uses four sorting algorithms: quicksort, mergesort, insertionsort, and bubblesort. In the following subsections, we'll give an overview of them.
+Sorting algorithms are widely used in many aspects of data processing, information searches, business finance, computer encryption, etc.
+This work uses four sorting algorithms: quicksort, mergesort, insertionsort, and bubblesort.
+In the following subsections, we'll give an overview of them.
 
@@
 
-Sorting algorithms are widely used in many aspects of data processing, information searches, business finance, computer encryption, etc.
-Quicksort algorithm, created by Hoare \cite{Hoare1962}, is considered as one of the fastest and best sorting algorithms \cite{Wang2011}.
-The algorithm is based on the paradigm of divide and conquer.
+Quicksort algorithm, created by Hoare \cite{Hoare1962}, is considered as one of the fastest and best sorting algorithms \cite{Wang2011}. The algorithm is based on the paradigm of divide and conquer.
 
-This algorithm has an execution time is $\theta(n^2)$ in the worst case over \textit{n} numbers as input.
+This algorithm has a execution time of $\theta(n^2)$ in the worst case over \textit{n} numbers as input.
 Despite that execution time, quicksort is often the best option for sorting because of its remarkable average efficiency: $\theta(n lg n)$ \cite{Cormen2009}.
@@
 Mergesort was invented by John Von Newman and is one of the most elegant algorithms to appear in the sorting literature.
-It is the first sorting algorithm to have $\theta(n lg n)$ time complexity bound.
+It is the first sorting algorithm to have $\theta(n lg n)$ execution time bound.
 It is important to observe that this algorithm spends a lot of time on data transfer operations.
@@
 
+This algorithm sorts the array by shifting the elements one at time.
+It is efficient in sorting a small number of elements.
+The overall execution time of this algorithm is $\theta(n^2)$ \cite{Cormen2009}.
+The basic sorting steps are:
+\begin{itemize}
+    \item If there are more than one element, pick the next element;
+    \item Compare with all the elements in sorted sub-list;
+    \item Shift all the elements in sorted sub-list that is greater than the value to be sorted;
+    \item Insert the value;
+    \item Repeat until list is sorted.
+\end{itemize}
+
 \subsection{Bubblesort}
+
+Bubblesort involves the repeated comparison and, if necessary, the exchange of adjacent elements.
+With this algorithm, the number of comparisons is always the same because the two for loops repeat the specified number of times whether the list is initially ordered or not \cite{NitinArora}.
+
+Table \ref{table1} below shows the time complexity comparison between the sorting algorithms presented.
+
+\begin{table}[htbp]
+    \caption{Sorting algorithms complexity time comparison \cite{Prajapati2017}}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    \multirow{2}{*}{\textbf{Algorithm}}&\multicolumn{3}{|c|}{\textbf{Time Complexity}} \\
+    \cline{2-4} 
+    & \textbf{\textit{Best Case}} & \textbf{\textit{Average Case}}& \textbf{\textit{Worst Case}} \\
+    \hline
+    Bubblesort & $O(n^2)$ & $O(n^2)$ & $O(n^2)$ \\
+    Insertionsort & $O(n)$ & $O(n^2)$ & $O(n^2)$ \\
+    Quicksort & $O(nlgn)$ & $O(nlgn)$ & $O(n^2)$ \\
+    Mergesort & $O(nlgn)$ & $O(nlgn)$ & $O(nlgn)$ \\
+    \hline
+    \end{tabular}
+    \label{table1}
+    \end{center}
+    \end{table}

### 2019-10-21 paper/SortingAlgorithms.tex
continuação da escrita da fundamntação. Adição de artigos para referências.

@@
 
-Bubblesort involves the repeated comparison and, if necessary, the exchange of adjacent elements.
-With this algorithm, the number of comparisons is always the same because the two for loops repeat the specified number of times whether the list is initially ordered or not \cite{NitinArora}.
+The bubble sort is the oldest and simplest sorting method in use.
+It works by comparing each item in the list with the item next to it, and swapping them if required.
+The algorithm repeats this process until it makes a pass all the way through the list without swapping any items (in other words, all items are in the correct order) \cite{Mansotra2011}.
 
-Table \ref{table1} below shows the time complexity comparison between the sorting algorithms presented.
+Table \ref{table1} below shows the time complexity comparison between the sorting algorithms presented. The \textit{n} is the number of input elements.
 

### 2019-10-21 paper/article.tex
continuação da escrita do documento
continuação da escrita do background
continuação da escrita da fundamntação. Adição de artigos para referências.

@@
-\documentclass[conference,onecolumn]{IEEEtran}
+\documentclass[11pt,conference,onecolumn]{IEEEtran}
 \IEEEoverridecommandlockouts
@@
 \usepackage{algorithmic}
+\usepackage{multirow}
 \usepackage{graphicx}
@@
 
-\title{Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Sorting algorithms: how are they affected by memory faults?}
 
@@
 
-\input{Background}
+\input{MemoryFaults}
+
+\input{SortingAlgorithms}
+
+\input{StudySettings}
 
@@
 
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-% \begin{thebibliography}{00}
-% \bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-% \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-% \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-% \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-% \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-% \bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-% \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-% \end{thebibliography}
-
 \bibliography{RM1_Assignment}
-\bibliographystyle{plain}
-
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliographystyle{ieeetr}
 

### 2019-12-04 _fabiano/python/01-CreateDatasetFromData.py
dados extraídos; criados arquivos CSV para usar no Python; com adicao da medida k_unordered_sequence

@@ -1,0 +1,95 @@
+import sys
+import os
+import shutil
+import datetime
+import time
+
+
+def calcular_k_unordered_sequence(data):
+    arr = data.split(' ')
+    #
+    indice1 = 0
+    indice2 = 1
+    indice_max = len(arr) - 1
+    k = 0
+    #
+    while (indice1 < indice_max):
+        #
+        if (int(arr[indice1]) > int(arr[indice2])):
+            k += 1
+        #
+        indice1 += 1
+        indice2 += 1
+    #
+    return k
+
+
+
+# define as pastas contendo os dados
+pasta_origem = '../data'
+pastas = os.listdir(pasta_origem)
+
+#abre o arquivo onde serao salvos os dados extraidos
+#se o arquivo ja existir, entao apaga e cria novamente
+path_arq_destino = '%s/_dados_extraidos.csv'%pasta_origem
+if os.path.exists(path_arq_destino):
+    os.remove(path_arq_destino)
+
+arq_destino = open(path_arq_destino, 'w+')
+arq_destino.write('%s;%s;%s;%s;%s;%s\n' % ('algoritmo', 'probabilidade_erro', 'size_of_array', 'largest_sorted_subarray', 'k_unordered_sequence', 'percentual_k_unordered') )
+
+#
+for pasta_prob_erro in pastas:
+    #teste para não pegar a pasta ".DStore" do macOS
+    if (pasta_prob_erro[0] not in ['.','_']):
+        prob_erro = pasta_prob_erro.split('-')[1].replace(' div ', '/')
+        pastas_prob_erro = '%s/%s' % (pasta_origem, pasta_prob_erro)
+        pastas = os.listdir(pastas_prob_erro)
+        print('*processando: prob. erro = %s' % prob_erro)
+        #
+        for pasta_algoritmo in pastas:
+            # teste para não pegar a pasta ".DStore" do macOS
+            if (pasta_algoritmo[0] != '.'):
+                algoritmo = pasta_algoritmo
+                pastas_algoritmo = '%s/%s' % (pastas_prob_erro, pasta_algoritmo)
+                # print(pastas_prob_erro,' || ', pastas_algoritmo)
+                pastas = os.listdir(pastas_algoritmo)
+                # print('    *processando: algoritmo = %s' % algoritmo)
+                #
+                for pasta_n in pastas:
+                    # teste para não pegar a pasta ".DStore" do macOS
+                    if (pasta_n[0] != '.'):
+                        n = pasta_n
[…]

### 2019-12-04 _fabiano/python/gen.py

@@ -1,0 +1,33 @@
+from random import *
+
+n_sizes = [100, 1000, 10000]
+#n_sizes = [1, 2, 3]
+
+for n in n_sizes:
+    #eps = 1.0/n
+    eps = 0.05
+    maxr = n/2
+    arq = "_data-005-%s.in"%(n)
+    f = open(arq,"w")
+    f.write(str(eps) + " " + str(n))
+    for i in range(n):
+        f.write(" " + str(randint(1,maxr)))
+    f.write("\n")
+    f.close()
+
+# ============================
+# CODIGO ANTERIOR
+# ============================
+# n = 10000
+# eps = 1.0/n
+# maxr = n/2
+
+# f = open("data2.in","w")
+# f.write(str(eps) + " " + str(n))
+
+# for i in range(n):
+#     f.write(" " + str(randint(1,maxr)))
+# f.write("\n")
+
+# f.close()
+

### 2019-12-04 _fabiano/python/main_execution.py

@@ -1,0 +1,47 @@
+    import sys
+    import os
+
+
+def main(sorting_alg, data_size, perc_rate, repetitions):
+    inFile = '_data-' + perc_rate + '-' + data_size + '.in'
+    path = os.getcwd() + '/data-' + perc_rate + '/' + sorting_alg + '/' + data_size
+    for n in range(0, int(repetitions)):
+        createDir(path, sorting_alg, data_size)
+        os.system('./' + sorting_alg + ' < ' + inFile + ' > ' + path + '/data-' + data_size + '-' + str(n+1) + '.out ')
+
+def createDir(path, sorting_alg, data_size):
+    if os.path.isdir(path) == False:
+        try:
+            os.makedirs(path)
+        except OSError as ose:
+            print ("Creation of the directory failed %s", path)
+            print (ose)
+        else:
+            print ("Successfully created the directory ")
+
+
+#print(os.path.dirname(os.path.abspath(__file__)))
+alg = [
+    'quick', 
+    'bubble', 
+    'merge', 
+    'insertion']
+perc_rate = [
+    'normal',
+    #'001',
+    #'002',
+    #'005'
+]
+d_size = ['100', '1000', '10000']
+repetitions = '1000'
+
+print('Iniciando execucao...')
+for n in alg:
+    print('Algoritmo: ' + n)
+    for p in perc_rate:
+        print('% Rate: ' + p)
+        for y in d_size:
+            print('Data Size: ' + y)
+            print('Repeticoes: ' + repetitions)
+            main(n, y, p, repetitions)
+print('Finalizando execucao...')

### 2019-12-04 _fabiano/python/01-CreateDatasetFromData.py
CSV contendo todos os dados e Jupyter-Notebook de testes

@@ -26,7 +26,7 @@ def calcular_k_unordered_sequence(data):
 
 
 # define as pastas contendo os dados
-pasta_origem = '../data'
+pasta_origem = '../../../../data'
 pastas = os.listdir(pasta_origem)
 
 #abre o arquivo onde serao salvos os dados extraidos
@@ -80,11 +80,10 @@ for pasta_prob_erro in pastas:
                             l4_largest_sorted_subarray = int(lines[3])
 
                             #se for a prob. erro default (1/n) ajusta a descricao no arquivo
-                            if (prob_erro == '1/n'):
-                                prob_erro_csv = '%g' % (1.0/int(n))
-                                # prob_erro_csv = '1/%s'% (n)
-                            else:
-                                prob_erro_csv = prob_erro
+                            prob_erro_csv = prob_erro
+                            # if (prob_erro == '1/n'):
+                            #     prob_erro_csv = '%g' % (1.0/int(n))
+
                             #
                             k_unordered_sequence = calcular_k_unordered_sequence(l2_sorting_with_fault)
                             #

### 2019-12-05 _fabiano/python/01-CreateDatasetFromData.py
modificacoes na geracao do CSV com os dados extraidos

@@ -36,7 +36,7 @@ if os.path.exists(path_arq_destino):
     os.remove(path_arq_destino)
 
 arq_destino = open(path_arq_destino, 'w+')
-arq_destino.write('%s;%s;%s;%s;%s;%s\n' % ('algoritmo', 'probabilidade_erro', 'size_of_array', 'largest_sorted_subarray', 'k_unordered_sequence', 'percentual_k_unordered') )
+arq_destino.write('%s;%s;%s;%s;%s;%s;%s\n' % ('algoritmo', 'probabilidade_erro', 'size_of_array', 'largest_sorted_subarray', 'k_unordered_sequence', 'percentual_k_unordered', 'percentual_maior_array') )
 
 #
 for pasta_prob_erro in pastas:
@@ -84,11 +84,15 @@ for pasta_prob_erro in pastas:
                             # if (prob_erro == '1/n'):
                             #     prob_erro_csv = '%g' % (1.0/int(n))
 
+
+                            #calcula o percentual do maior array
+                            percentual_maior_array = 100.0 * int(l4_largest_sorted_subarray) / int(n)
+
                             #
                             k_unordered_sequence = calcular_k_unordered_sequence(l2_sorting_with_fault)
                             #
                             percentual_k_unordered = 100.0 * int(k_unordered_sequence) / int(n)
                             #
-                            arq_destino.write( '%s;%s;%s;%s;%s;%.2f\n' % (algoritmo, prob_erro_csv, n, l4_largest_sorted_subarray, k_unordered_sequence, percentual_k_unordered ))
+                            arq_destino.write( '%s;%s;%s;%s;%s;%.2f;%.2f\n' % (algoritmo, prob_erro_csv, n, l4_largest_sorted_subarray, k_unordered_sequence, percentual_k_unordered, percentual_maior_array ))
 
                             # break

### 2019-12-06 sorting/main_execution.py
arquivos com 3000 repeticoes para o quick

@@ -22,10 +22,10 @@ def createDir(path, sorting_alg, data_size):
 
 #print(os.path.dirname(os.path.abspath(__file__)))
 alg = [
-    #'quick', 
+    'quick', 
     #'bubble', 
     #'merge', 
-    'insertion'
+    #'insertion'
     ]
 perc_rate = [
     'normal',

### 2019-12-06 sorting/main_execution.py
arquivos com 3000 repeticoes para o bubble

@@ -22,8 +22,8 @@ def createDir(path, sorting_alg, data_size):
 
 #print(os.path.dirname(os.path.abspath(__file__)))
 alg = [
-    'quick', 
-    #'bubble', 
+    #'quick', 
+    'bubble', 
     #'merge', 
     #'insertion'
     ]

### 2019-12-06 sorting/main_execution.py
arquivos com 3000 repeticoes para o merge

@@ -23,8 +23,8 @@ def createDir(path, sorting_alg, data_size):
 #print(os.path.dirname(os.path.abspath(__file__)))
 alg = [
     #'quick', 
-    'bubble', 
-    #'merge', 
+    #'bubble', 
+    'merge', 
     #'insertion'
     ]
 perc_rate = [

### 2019-12-06 sorting/main_execution.py
arquivos com 3000 repeticoes para o insertion

@@ -24,8 +24,8 @@ def createDir(path, sorting_alg, data_size):
 alg = [
     #'quick', 
     #'bubble', 
-    'merge', 
-    #'insertion'
+    #'merge', 
+    'insertion'
     ]
 perc_rate = [
     'normal',

### 2019-12-06 _fabiano/python/01-CreateDatasetFromData.py
finalizado: dados para analisar (com 60 mil linhas)

@@ -81,8 +81,8 @@ for pasta_prob_erro in pastas:
 
                             #se for a prob. erro default (1/n) ajusta a descricao no arquivo
                             prob_erro_csv = prob_erro
-                            # if (prob_erro == '1/n'):
-                            #     prob_erro_csv = '%g' % (1.0/int(n))
+                            if (prob_erro == '1/n'):
+                                prob_erro_csv = '%g' % (1.0/int(n))
 
 
                             #calcula o percentual do maior array

### 2019-12-06 paper/MaterialsAndMethods.tex
mudança na estrutura do artigo

\section{Materials and Methods}

\subsection{Experimental Data}

\subsection{Hypothesis}

\subsection{Linear Regression}

### 2019-12-09 paper/MaterialsAndMethods.tex

@@
 
+We first describe our data, showing all its characteristics. Then, we provide our hypothesis, define the setup, and perform the testing. Finally, we collect and perform data and regression analysis.
+
 \subsection{Experimental Data}
+
+To conduct the proposed study we get a set of files with the basic setup and instructions, that was composed by:
+\begin{itemize}
+    \item A file that contains a sequence of integers that are the input data;
+    \item Four files, one for each os those algorithms: quicksort, bubblesort, insertion sort, and mergesort, that are used to sorting the input data;
+    \item An output file with the sorted data.
+\end{itemize}
+
+Falar das variaveis dependentes e independentes...
+
+From that, we develop a Python script to generate custom inputs.
+The sequence has two characteristics: (\textit{i}) the sequence size, and (\textit{ii}) the probability of failure.
+For this work, the generated input files are shown in the table \ref{table2} below.
+
+\begin{table}[htbp]
+    \caption{Generated input data.}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    \multirow{1}{*}{\textbf{Input}}&\textbf{Sequence Size}&\textbf{Probability of Failure} \\
+    \hline
+    Input A & 100 & 1\% \\
+    Input B & 100 & 2\% \\
+    Input C & 100 & 5\% \\
+    \hline
+    Input D & 1000 & 1\% \\
+    Input E & 1000 & 2\% \\
+    Input F & 1000 & 5\% \\
+    \hline
+    Input G & 10000 & 1\% \\
+    Input H & 10000 & 2\% \\
+    Input I & 10000 & 5\% \\
+    \hline
+    \end{tabular}
+    \label{table2}
+    \end{center}
+\end{table}
+
+The input file looks like follow:
+
+\begin{verbbox}[\mbox{}]
+0.01 100 9 48 37 6 26 7 24 44 17 50 48 30 49 33 22 13 42 29 39 13 19 13 9 28 
+34 1 33 27 14 45 48 40 11 17 6 50 9 44 20 16 37 45 23 14 38 29 10 49 44 46 35
+45 15 2 22 1 46 40 8 48 23 23 32 35 3 15 8 36 17 24 27 48 28 5 28 50 44 4 25 
+6 9 1 11 44 26 50 44 12 7 20 30 20 37 20 6 8 13 15 20 49
+\end{verbbox}
+
+\begin{figure}[hbtp]
+    \centering
+    \fbox{
+    \theverbbox
+    }
+    \caption{Example of input file.}
+    \label{input-file-example}
+\end{figure}
+
+Figure \ref{input-file-example} shows an example of an input file generated by the Python script.
+The first number of the sequence (\texttt{0.01}) is the probability of memory failure when sorting.
+The second number (\texttt{100}) means the size of the integers sequence used by sorting.
+The rest of the numbers indicates the sequence itself.
 

### 2019-12-10 _fabiano/python/02-Medias_por_algoritmo_e_prob_erro.py
gerados graficos estatisticos por algoritmo e prob. erro
contendo barplot, media, desvio padrao, min e max

@@ -1,0 +1,171 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+
+# %matplotlib inline
+
+# ========================================================
+# estilos de graficos :
+# >>  https://tonysyu.github.io/raw_content/matplotlib-style-gallery/gallery.html
+# ========================================================
+# plt.style.use('seaborn-whitegrid')
+# plt.style.use('seaborn-pastel')
+# plt.style.use('seaborn-colorblind')
+# plt.style.use('seaborn-bright')
+# plt.style.use('grayscale')
+# plt.style.use('ggplot')
+# plt.style.use('fivethirtyeight')
+# plt.style.use('dark_background')
+# plt.style.use('classic')
+# plt.style.use('bmh')
+
+
+
+pasta_origem = '../data/data_grouped'
+arq_metadata = open('%s/_metadata.csv' % (pasta_origem), 'w+')
+
+probs = ['0.01','0.02','0.05','0.001','0.0001']
+# probs = ['0.01']#,'0.02']#,'0.05','0.001','0.0001']
+
+sizes = ['100','1000','10000']
+
+df_tudo = pd.DataFrame()
+
+for prob in probs:
+    for size in sizes:
+        filtro_arq = '%s_%s_' % (prob, size)
+
+        arqs_in = os.listdir(pasta_origem)
+        for f in arqs_in:
+            if (f.startswith(filtro_arq)):
+                print(f)
+                csv = os.path.join(pasta_origem, f)
+                df_temp = pd.read_csv(delimiter = ';', filepath_or_buffer = csv)
+                df_tudo = df_tudo.append(df_temp)
+
+#ordena os registros por algoritmo
+df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+
+
+# gera os graficos
+rows = 5
+cols = 2
+
+larg_fig = 32
+alt_fig  = 41
+font_size = 15
+
+sns_palette = 'Set2'
+color_map = sns.color_palette(sns_palette, n_colors=4)
+
+
+for prob in probs:
+    data = df_tudo[df_tudo.probabilidade_erro == float(prob)]
+
+    df_means = data.groupby(['size_of_array', 'algoritmo']).mean()
[…]

### 2019-12-10 _fabiano/python/teste-1.py

@@ -1,0 +1,87 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+
+
+pasta_origem = '../data/data_grouped'
+arq_metadata = open('%s/_metadata.csv' % (pasta_origem), 'w+')
+
+probs = ['0.01','0.02','0.05','0.001','0.0001']
+probs = ['0.01']#,'0.02']#,'0.05','0.001','0.0001']
+sizes = ['100','1000','10000']
+
+df_tudo = pd.DataFrame()
+
+for prob in probs:
+    for size in sizes:
+        filtro_arq = '%s_%s_' % (prob, size)
+
+        arqs_in = os.listdir(pasta_origem)
+        for f in arqs_in:
+            if (f.startswith(filtro_arq)):
+                csv = os.path.join(pasta_origem, f)
+                df_temp = pd.read_csv(delimiter = ';', filepath_or_buffer = csv)
+                df_tudo = df_tudo.append(df_temp)
+
+#ordena os registros por algoritmo
+df_tudo = df_tudo[['algoritmo','size_of_array', 'percentual_k_unordered','percentual_maior_array']]
+df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+
+# print(df_tudo.head())
+
+df_means = df_tudo.groupby(['size_of_array','algoritmo']).mean()
+print(df_means.head())
+
+data = df_means['percentual_k_unordered'].unstack()
+print(data)
+
+data.plot(kind='bar')
+plt.show()
+
+
+# print(data.columns)
+# print(type(data))
+# print(type(data['bubble']))
+# data
+#
+# sns.lineplot(data=data )
+# sns.barplot(data=data)
+# plt.show()
+
+# print (df_means.columns )
+# print (df_means.unstack())
+# print (df_means.head(20) )
+
+
+# df_std = df_tudo.groupby(by='algoritmo').std()
+# print (df_std.head() )
+#
+# df_median = df_tudo.groupby(by='algoritmo').median()
+# print (df_median.head() )
+#
+# df_var = df_tudo.groupby(by='algoritmo').var()
+# print (df_var.head() )
+#
+# df_min = df_tudo.groupby(by='algoritmo').min()
[…]

### 2019-12-10 _fabiano/python/util_graficos.py

@@ -1,0 +1,28 @@
+# imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+
+
+def gerarBarplot(data, x, y, hue, title='', order=None, palette='Blues'):
+    #retorna objeto 'ax'
+    return sns.barplot(x=x,
+                       y=y,
+                       hue=hue,
+                       data=data,
+                       palette=palette,
+                       order=order,
+                       capsize=0.05,
+                       saturation=8,
+                       errcolor='gray',
+                       errwidth=2,
+                       ci='sd'
+                       ).set_title(title)
+
+

### 2019-12-10 _fabiano/python/02-Medias_por_algoritmo_e_prob_erro.py
alguns testes realizados

@@ -83,7 +83,6 @@ for prob in probs:
     if (data.shape[0] > 0):
         # print(data.head())
 
-
         graf_title = 'Estatísticas por Algoritmo para Probabilidade de Erro %s' % (prob)
         file_title = 'Estatisticas_por_Algoritmo_Prob_%s' % (prob)
 

### 2019-12-10 _fabiano/python/teste-2.py

@@ -1,0 +1,60 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+from scipy.stats.distributions import norm
+
+from scipy.stats import kde
+
+x1 = np.random.normal(-1, 0.5, 15)
+
+# parameters: (loc=0.0, scale=1.0, size=None)
+
+x2 = np.random.normal(6, 1, 10)
+y = np.r_[x1, x2]
+
+# r_ Translates slice objects to concatenation along the first axis.
+
+x = np.linspace(min(y), max(y), 100)
+s = 0.4   # Smoothing parameter
+
+kernels = np.transpose([norm.pdf(x, yi, s) for yi in y])
+
+# Calculate the kernels
+density = kde.gaussian_kde(y)
+
+# plt.plot(x, kernels, 'k:')
+# plt.plot(x, kernels.sum(1), 'r')
+# plt.plot(y, np.zeros(len(y)), 'bo', ms=10)
+
+xgrid = np.linspace(x.min(), x.max(), 200)
+# plt.hist(y, bins=28, normed=True)
+# plt.plot(xgrid, density(xgrid), 'r-')
+
+# Create a bi-modal distribution with a mixture of Normals.
+
+x1 = np.random.normal(-1, 2, 15) # parameters: (loc=0.0, scale=1.0, size=None)
+x2 = np.random.normal(6, 3, 10)
+
+# Append by row
+x = np.r_[x1, x2]
+
+# r_ Translates slice objects to concatenation along the first axis.
+# plt.hist(x, bins=18, normed=True)
+
+
+density = kde.gaussian_kde(x)
+xgrid = np.linspace(x.min(), x.max(), 200)
+plt.hist(x, bins=18, normed=True)
+plt.plot(xgrid, density(xgrid), 'r-')
+
+plt.show()

### 2019-12-10 _fabiano/python/teste-3.py

@@ -1,0 +1,54 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+import util_ler_dados as udata
+from scipy.stats.distributions import norm
+
+from scipy.stats import kde
+
+df = udata.obterDados()
+
+# for prob in udata.PROBABILIDADES:
+df_prob = udata.filtrarPorProbabilidadeErro(df, '0.01')
+print( df_prob.shape)
+print( df_prob['algoritmo'].unique())
+
+# print( df_prob.groupby(['size_of_array', 'algoritmo']).count().head() )
+
+sns.lmplot(x='percentual_k_unordered',
+           hue='algoritmo',
+           y='percentual_maior_array',
+           data=df,
+           # markers=['o','v','+','x'],
+           scatter_kws={'s': 5},
+           col='algoritmo',
+           row='probabilidade_erro', # 'size_of_array',
+           height=3,
+           )
+
+# plt.show()
+file_title = 'teste-03-lmplot'
+plt.savefig('graficos/_%s.png' % (file_title), bbox_inches='tight',
+            pad_inches=2)  # , format='png', orientation='landscape', papertype='letter')
+
+# print( df.head() )
+#
+# df1 = udata.filtrarPorProbabilidadeErro(df, '0.02')
+# print( df1.head() )
+#
+# df2 = udata.filtrarPorAlgoritmo(df1, 'merge')
+# print( df2.head() )
+#
+# df_means, df_std, df_min, df_max, df_var = udata.obterEstatisticasPorTamanho_Algoritmo(df1)
+# print( df_means.head() )
+

### 2019-12-10 _fabiano/python/teste-4-correlacao.py

@@ -1,0 +1,58 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+import util_ler_dados as udata
+from scipy.stats.distributions import norm
+
+from scipy.stats import kde
+
+def salvarGrafico(df_p, file_title, tam):
+    # df_p.loc[:]['size_of_array'] = tam
+    print(df_p['size_of_array'].unique())
+    corr = df_p.corr()#.round(decimal=3)
+    print(corr)
+    fig = plt.figure()
+    sns.heatmap(corr, annot=True)#, cmap='coolwarm')
+    fig.savefig('graficos/_%s.png' % (file_title), bbox_inches='tight',
+                pad_inches=2)  # , format='png', orientation='landscape', papertype='letter')
+    plt.close(fig)
+
+q1 = udata.obterDados()
+q1 = udata.filtrarPorTamanhoArray(q1, 100)
+print(q1.corr())
+
+df = udata.obterDados()
+# salvarGrafico(df=df, file_title='teste-04-correlacao-0-geral')
+
+for prob in udata.PROBABILIDADES:
+    df_prob = udata.filtrarPorProbabilidadeErro(df, prob)
+    # print( df_prob.shape )
+    # print(df_alg.shape)
+    for tam in udata.TAMANHOS:
+        # print('%.2f-%s-%s' % (prob, alg, tam))
+        df_tam = udata.filtrarPorTamanhoArray(df_prob, tam)
+        for alg in udata.ALGORTIMOS:
+            df_alg = udata.filtrarPorAlgoritmo(df_tam, alg)
+            # print(df_tam.head())
+            # print(df_tam.shape)
+            # print('')
+            # se tiver dados no DF
+            if (df_alg.shape[0] > 0):
+                print(df_alg.head())
+                df_alg.loc[:]['size_of_array'] = tam * 1.0
+                file_title = 'teste-04-correlacao-%s-%s-%s' % (prob, alg, tam)
+                salvarGrafico(df_p=df_alg, file_title=file_title, tam=int(tam))
+                break
+            break
+        break
+    break

### 2019-12-10 _fabiano/python/util_ler_dados.py

@@ -1,0 +1,59 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+
+PROBABILIDADES = ['0.01', '0.02', '0.05', '0.001', '0.0001']
+
+TAMANHOS = [100, 1000, 10000]
+
+ALGORTIMOS = ['bubble', 'merge', 'quick', 'insertion']
+
+def obterDados(probs = [0.01, 0.02, 0.05, 0.001, 0.0001], sizes=[100, 1000, 10000]):
+    pasta_origem = '../data/data_grouped'
+    arq_metadata = open('%s/_metadata.csv' % (pasta_origem), 'w+')
+
+    df_tudo = pd.DataFrame()
+
+    for prob in probs:
+        for size in sizes:
+            filtro_arq = '%s_%s_' % (prob, size)
+
+            arqs_in = os.listdir(pasta_origem)
+            for f in arqs_in:
+                if (f.startswith(filtro_arq)):
+                    # print(filtro_arq)
+                    csv = os.path.join(pasta_origem, f)
+                    df_tudo = df_tudo.append( pd.read_csv(delimiter=';', filepath_or_buffer=csv) )
+
+    return df_tudo
+
+
+def filtrarPorProbabilidadeErro(df, prob):
+    if (type(prob) != float):
+        prob = float(prob)
+
+    return df[df.probabilidade_erro == prob]
+
+def filtrarPorAlgoritmo(df, algoritmo):
+    return df[df.algoritmo == algoritmo]
+
+def filtrarPorTamanhoArray(df, tamanho):
+    return df[df['size_of_array'] == tamanho]
+
+def obterEstatisticasPorTamanho_Algoritmo(df):
+    df_means = df.groupby(['size_of_array', 'algoritmo']).mean()
+    df_std = df.groupby(['size_of_array', 'algoritmo']).std()
+    df_min = df.groupby(['size_of_array', 'algoritmo']).min()
+    df_max = df.groupby(['size_of_array', 'algoritmo']).max()
+    df_var = df.groupby(['size_of_array', 'algoritmo']).var()
+    return df_means, df_std, df_min, df_max, df_var

### 2019-12-12 _fabiano/python/03-Medias_por_algoritmo_e_prob_erro_juntando_todos_tamanhos.py
gerados os graficos e os CSVs para análise

@@ -41,6 +41,7 @@ sizes = ['100','1000','10000']
 
 df_tudo = pd.DataFrame()
 
+#le os arquivos de entrada
 for prob in probs:
     for size in sizes:
         filtro_arq = '%s_%s_' % (prob, size)
@@ -76,10 +77,11 @@ df_dados_csv = pd.DataFrame()
 for prob in probs:
     data = df_tudo[df_tudo.probabilidade_erro == float(prob)]
 
-    df_means = data.groupby(['size_of_array', 'algoritmo']).mean()
-    df_std = data.groupby(['size_of_array', 'algoritmo']).std()
-    df_min = data.groupby(['size_of_array', 'algoritmo']).min()
-    df_max = data.groupby(['size_of_array', 'algoritmo']).max()
+    group_by = ['probabilidade_erro', 'algoritmo']
+    df_means = data.groupby(group_by).mean()
+    df_std = data.groupby(group_by).std()
+    df_min = data.groupby(group_by).min()
+    df_max = data.groupby(group_by).max()
 
     # colunas_join = ['largest_sorted_subarray','k_unordered_sequence','percentual_k_unordered','percentual_maior_array']
     colunas_join = ['percentual_k_unordered','percentual_maior_array']
@@ -94,38 +96,38 @@ for prob in probs:
     if (data.shape[0] > 0):
         # print(data.head())
 
-        file_title = 'Estatisticas_por_Algoritmo_Prob_%s' % (prob)
+        file_title = 'Estatisticas_por_Algoritmo_Juntando_os_Tamanhos_Prob_%s' % (prob)
 
         if (gerar_csvs_com_dados_dos_graficos):
             df_dados_csv.to_csv('graficos/comparacao_entre_algoritmos/csv/%s.csv' % (file_title))
 
         if (gerar_graficos):
-            graf_title = 'Estatísticas por Algoritmo para Probabilidade de Erro %s' % (prob)
+            graf_title = 'Estatísticas por Algoritmo Juntando Todos os Tamanhos - Probabilidade de Erro %s' % (prob)
+
             fig = plt.figure(figsize=[larg_fig, alt_fig])
             plt.suptitle(graf_title + '\nBarplot / Média / Desvio Padrão / Mín. / Máx.', fontsize=30)
             plt.rcParams.update({'font.size': font_size})
 
-
             #grafico de barras para % Desordenados
             ax = plt.subplot(rows, cols, indx)
-            graf.gerarBarplot(ax=ax, x='size_of_array',
[…]

### 2019-12-12 _fabiano/python/teste-1.py

@@ -39,13 +39,22 @@ df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[T
 
 # print(df_tudo.head())
 
-df_means = df_tudo.groupby(['size_of_array','algoritmo']).mean()
+df_means = df_tudo.groupby('algoritmo').mean()
 print(df_means.head())
 
-data = df_means['percentual_k_unordered'].unstack()
+data = df_means['percentual_k_unordered']
 print(data)
 
-data.plot(kind='bar')
+# plt.figure(figsize=(12, 8))
+ax = data.plot(kind='bar')
+
+rects = ax.patches
+# Make some labels.
+labels = ["%.2f" % i for i in data.values]
+ax.set_xticklabels(labels)
+for rect, label in zip(rects, labels):
+    height = rect.get_height()
+    ax.text(rect.get_x() + rect.get_width() / 2.0, 0.5, label, ha='center', va='bottom')
 plt.show()
 
 

### 2019-12-12 _fabiano/python/util_graficos.py

@@ -10,19 +10,33 @@ import pandas as pd
 import seaborn as sns
 
 
-def gerarBarplot(data, x, y, hue, title='', order=None, palette='Blues'):
+def gerarBarplot(ax, data, x, y, hue, title='', order=None, palette='Blues'):
     #retorna objeto 'ax'
-    return sns.barplot(x=x,
-                       y=y,
-                       hue=hue,
-                       data=data,
-                       palette=palette,
-                       order=order,
-                       capsize=0.05,
-                       saturation=8,
-                       errcolor='gray',
-                       errwidth=2,
-                       ci='sd'
-                       ).set_title(title)
+    sns.barplot(ax=ax,
+                x=x,
+                y=y,
+                hue=hue,
+                data=data,
+                palette=palette,
+                order=order,
+                capsize=0.05,
+                saturation=8,
+                errcolor='gray',
+                errwidth=2,
+                ci='sd'
+                ).set_title(title)
 
+    return ax
 
+def inserirValoresNasBarras(ax, values):
+    rects = ax.patches
+    labels = ["%.2f" % i for i in values]
+    for rect, label in zip(rects, labels):
+        height = rect.get_height()
+        ax.text(rect.get_x() + rect.get_width() / 2.0, height * 1.01, label, ha='center', va='bottom')
+
+def inserirValoresNoBarplot(ax):
+    rects = ax.patches
+    for rect in rects:
+        height = rect.get_height()
+        ax.text(rect.get_x() + rect.get_width() / 2.0, height * 1.01, '%.2f'%(height), ha='center', va='bottom')

### 2019-12-15 paper/MaterialsAndMethods.tex
continuação da escrita

@@
 
-We first describe our data, showing all its characteristics. Then, we provide our hypothesis, define the setup, and perform the testing. Finally, we collect and perform data and regression analysis.
+We first state our problem, then describe our data, showing all its characteristics.
+Then, we provide our hypothesis, define the setup, and perform the testing.
+Finally, we collect and perform data and regression analysis.
 
-\subsection{Experimental Data}
+\subsection{Problem Statement}
+
+As introduced in the first section of this paper, sorting is a fundamental concept and essential for solving other problems.
+The content of memory location can change unexpectedly, i.e., faults may happen at any time.
+Considering this, the main objective of this work is to design experiments to answer the following research question:
+
+\begin{itemize}
+    \item \textit{RQ1:} How are sorting algorithms affected by memory faults?
+\end{itemize}
+
+\subsection{Variables}
+
+For this experimental study, we assume that the dependent and independent variables are as shown in Table \ref{table-variables} below:
+
+\begin{table}[htbp]
+    \caption{Dependent and independent variables.}
+    \begin{center}
+    \begin{tabular}{|c|c|}
+    \hline
+    \multicolumn{2}{|c|}{\textbf{Variables}}\\
+    \hline
+    \textbf{\textit{Dependent}} & \textbf{\textit{Independent}} \\
+    \hline
+    Largest subarray size & Probability of failure \\
+    Percentage of largest subarray size related to the original array & Array size \\
+    Unordered elements size & Sorting algorithm \\
+    Percentage of unordered elements size related to the original array & \\
+    \hline
+    \end{tabular}
+    \label{table-variables}
+    \end{center}
+\end{table}
+
+\subsection{Hypothesis}
+
+We define a set of hypothesis to test and draw some conclusions. They are:
+
+\setcounter{hyp}{-1}
+\begin{hyp}[Test hypothesis] \label{hyp:a}There is no difference in memory faults between tested algorithms.\end{hyp}
+\begin{hyp} \label{hyp:b}There are differences in memory faults between tested algorithms. \end{hyp}
+\begin{hyp} \label{hyp:c} An algorithm is better than others considering all dependent variables. \end{hyp}
+
+\begin{hyp} \label{hyp:d} ... \end{hyp}
+
+\subsection{Experimental Setup}
+
+\subsection{Development}
 
@@
 
-Falar das variaveis dependentes e independentes...
+\subsection{Data Analysis}
+
+\subsection{Conclusions}
 
@@
 The sequence has two characteristics: (\textit{i}) the sequence size, and (\textit{ii}) the probability of failure.
-For this work, the generated input files are shown in the table \ref{table2} below.
+For this work, the generated input files are shown in the Table \ref{table-input-data} below.
 
@@
     \end{tabular}
-    \label{table2}
+    \label{table-input-data}
     \end{center}
@@
 The rest of the numbers indicates the sequence itself.
-
-\subsection{Hypothesis}
-
-\subsection{Linear Regression}

### 2019-12-15 paper/article.tex
mudança na estrutura do artigo
inicio da escrita da parte especifica do estudo
continuação da escrita

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{amsthm}
+\usepackage{amsmath,amssymb,amsfonts}
 \usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
 \usepackage{algorithmic}
@@
 \usepackage{setspace}
+\usepackage{verbatimbox}
+\usepackage{thmtools}
+
+\declaretheoremstyle[spaceabove=6pt, spacebelow=6pt,headfont=\normalfont\bfseries,notefont=\mdseries, notebraces={(}{)},bodyfont=\normalfont,postheadspace=0.6em,
+headpunct=:]{mystyle}
+\declaretheorem[style=mystyle, name=Hypothesis, preheadhook={\renewcommand{\thehyp}{H\textsubscript{\arabic{hyp}}}}]{hyp}
+
+\usepackage{cleveref}
+\crefname{hyp}{hypothesis}{hypotheses}
+\Crefname{hyp}{Hypothesis}{Hypotheses}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\input{StudySettings}
+\input{MaterialsAndMethods}
+
+\input{Results}
+
+\input{Discussion}
+
+\input{Conclusion}
 

### 2019-12-15 _fabiano/python/04-Distribuicao_das_medidas_escolhidas.py
gerados intervalos de confianca

@@ -1,0 +1,198 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+
+# %matplotlib inline
+
+# ========================================================
+# estilos de graficos :
+# >>  https://tonysyu.github.io/raw_content/matplotlib-style-gallery/gallery.html
+# ========================================================
+# plt.style.use('seaborn-whitegrid')
+# plt.style.use('seaborn-pastel')
+# plt.style.use('seaborn-colorblind')
+# plt.style.use('seaborn-bright')
+# plt.style.use('grayscale')
+# plt.style.use('ggplot')
+# plt.style.use('fivethirtyeight')
+# plt.style.use('dark_background')
+# plt.style.use('classic')
+# plt.style.use('bmh')
+
+
+
+pasta_origem = '../data/data_grouped'
+arq_metadata = open('%s/_metadata.csv' % (pasta_origem), 'w+')
+
+probs = ['0.01','0.02','0.05','0.001','0.0001']
+# probs = ['0.01']#,'0.02']#,'0.05','0.001','0.0001']
+
+sizes = ['100','1000','10000']
+
+df_tudo = pd.DataFrame()
+
+#le os arquivos de entrada
+for prob in probs:
+    for size in sizes:
+        filtro_arq = '%s_%s_' % (prob, size)
+
+        arqs_in = os.listdir(pasta_origem)
+        for f in arqs_in:
+            if (f.startswith(filtro_arq)):
+                print(f)
+                csv = os.path.join(pasta_origem, f)
+                df_temp = pd.read_csv(delimiter = ';', filepath_or_buffer = csv)
+                df_tudo = df_tudo.append(df_temp)
+
+#ordena os registros por algoritmo
+df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+
+
+# gera os graficos
+rows = 5
+cols = 2
+
+larg_fig = 32
+alt_fig  = 41
+font_size = 15
+
+sns_palette = 'Set2'
+color_map = sns.color_palette(sns_palette, n_colors=4)
+
+gerar_graficos = True
+gerar_csvs_com_dados_dos_graficos = True
+
+df_dados_csv = pd.DataFrame()
+
+for prob in probs:
[…]

### 2019-12-15 _fabiano/python/teste-5-distribuicao_das_medidas.py

@@ -1,0 +1,96 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+import util_ler_dados as udata
+from scipy.stats.distributions import norm
+
+from scipy.stats import kde
+
+def salvarGrafico(df, file_title, tam, prob, alg, bins=30):
+
+    # numeros = df['percentual_maior_array']
+
+    fig = plt.figure(figsize=[20, 15])
+    plt.suptitle('%s - Prob. Erro: %s - Tam. Array: %s'%(alg, str(prob), str(tam)) )
+
+    numeros = df['percentual_k_unordered']
+    ax = plt.subplot(2,2,1)
+    # ax.set_xlabel('% Desornados', labelpad=10, weight='bold', size=9)
+    plt.title('% Desordenados')
+    sns.distplot(numeros, ax=ax, bins=bins, hist=True, kde=False)
+
+    ax = plt.subplot(2,2,2)
+    # ax.set_xlabel('% Desornados', labelpad=10, weight='bold', size=9)
+    plt.title('% Desordenados (KDE)')
+    sns.distplot(numeros, ax=ax, bins=bins, hist=True, kde=True)
+
+    numeros = df['percentual_maior_array']
+    ax = plt.subplot(2,2,3)
+    # ax.set_xlabel('% Maior Array', labelpad=10, weight='bold', size=9)
+    plt.title('% Maior Array')
+    sns.distplot(numeros, ax=ax, bins=bins, hist=True, kde=False)
+
+    ax = plt.subplot(2,2,4)
+    # ax.set_xlabel('% Maior Array', labelpad=10, weight='bold', size=9)
+    plt.title('% Maior Array (KDE)')
+    sns.distplot(numeros, ax=ax, bins=bins, hist=True, kde=True)
+
+    fig.savefig('graficos/distribuicao_medidas/_%s.png' % (file_title), bbox_inches='tight',
+                pad_inches=2)  # , format='png', orientation='landscape', papertype='letter')
+    plt.close(fig)
+    # plt.show()
+
+    # fig = plt.figure(figsize=[40, 50])
+    # plt.title('Prob. Erro: %s - Tam. Array: %s'%(str(prob), str(tam)) )
[…]

### 2019-12-15 paper/MaterialsAndMethods.tex

@@
 
-\subsection{Development}
-
 To conduct the proposed study we get a set of files with the basic setup and instructions, that was composed by:
@@
 \end{itemize}
-
-\subsection{Data Analysis}
-
-\subsection{Conclusions}
-
-From that, we develop a Python script to generate custom inputs.
-The sequence has two characteristics: (\textit{i}) the sequence size, and (\textit{ii}) the probability of failure.
-For this work, the generated input files are shown in the Table \ref{table-input-data} below.
-
-\begin{table}[htbp]
-    \caption{Generated input data.}
-    \begin{center}
-    \begin{tabular}{|c|c|c|c|}
-    \hline
-    \multirow{1}{*}{\textbf{Input}}&\textbf{Sequence Size}&\textbf{Probability of Failure} \\
-    \hline
-    Input A & 100 & 1\% \\
-    Input B & 100 & 2\% \\
-    Input C & 100 & 5\% \\
-    \hline
-    Input D & 1000 & 1\% \\
-    Input E & 1000 & 2\% \\
-    Input F & 1000 & 5\% \\
-    \hline
-    Input G & 10000 & 1\% \\
-    Input H & 10000 & 2\% \\
-    Input I & 10000 & 5\% \\
-    \hline
-    \end{tabular}
-    \label{table-input-data}
-    \end{center}
-\end{table}
 
@@
 
-Figure \ref{input-file-example} shows an example of an input file generated by the Python script.
-The first number of the sequence (\texttt{0.01}) is the probability of memory failure when sorting.
-The second number (\texttt{100}) means the size of the integers sequence used by sorting.
-The rest of the numbers indicates the sequence itself.
+The input data shown in the Figure \ref{input-file-example} is divided as follows:
+
+\begin{itemize}
+    \item \textit{Probability of Failure}: the first number of the sequence (\texttt{0.01}) is the probability of memory failure when sorting;
+    \item \textit{Sequence size}: the second number (\texttt{100}) means the size of the integers sequence used by sorting;
+    \item \textit{Sequence}: the rest of the numbers indicates the sequence itself.
+\end{itemize}
+
+We run 1000 times each algorithm with each file listed in Table \ref{table-input-data} below.
+We chose this number of executions to reduce possible noise in the generated data.
+Table \ref{table-input-data} shows 9 different input files with its sequence sizes and probabilities of failure.
+Plus, the number of executions and each sorting algorithm.
+
+For example, Input A showed in that table with its characteristics was executed 1000 times for each algorithm -  bubblesort, quicksort, mergesort, and insertion sort - totalizing 4000 executions.
+
+\begin{table}[H]
+    \caption{Generated input data.}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    \textbf{Input} & \textbf{Sequence Size} & \textbf{Probability of Failure} & \textbf{Executions} & \textbf{Algorithm} \\ 
+    \hline
+    \multirow{4}{*}{Input A} & \multirow{4}{*}{100} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input B} & \multirow{4}{*}{100} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input C} & \multirow{4}{*}{100} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input D} & \multirow{4}{*}{1000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input E} & \multirow{4}{*}{1000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input F} & \multirow{4}{*}{1000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input G} & \multirow{4}{*}{10000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input H} & \multirow{4}{*}{10000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \multirow{4}{*}{Input I} & \multirow{4}{*}{10000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+    & & & & Quicksort \\
+    & & & & Mergesort \\
+    & & & & Insertion Sort \\
+    \hline
+    \end{tabular}
+    \label{table-input-data}
+    \end{center}
+\end{table}
+
+Each execution generates an output file.
+Then, we generate 4000 outputs for each combination of sequence size, and the probability of failure, totalizing 36000 files.
+Figure \ref{output-file-example} shows an output file.
+
+\begin{verbbox}[\mbox{}]
+[1]  9 48 37 6 26 7 24 44 17 50 48 30 49 33 22 13 42 29 39 13 19 13 9 28 34 1
+33 27 14 45 48 40 11 17 6 50 9 44 20 16 37 45 23 14 38 29 10 49 44 46 35 45  
+15 2 22 1 46 40 8 48 23 23 32 35 3 15 8 36 17 24 27 48 28 5 28 50 44 4 25 6 9
+1 11 44 26 50 44 12 7 20 30 20 37 20 6 8 13 15 20 49
+[2]  1 1 1 2 3 4 5 6 6 6 6 7 7 8 8 8 9 9 9 9 10 11 11 12 13 13 13 13 14 14 15 
+15 15 16 17 17 17 19 20 20 20 20 22 22 23 23 23 24 24 25 26 26 27 27 28 28 28 
+29 29 30 30 32 33 33 34 35 35 36 37 37 37 38 39 40 40 42 44 44 44 44 44 44 20 
+45 45 45 46 46 48 48 48 48 48 49 49 50 49 50 50 50
+[3]  1 1 1 2 3 4 5 6 6 6 6 7 7 8 8 8 9 9 9 9 10 11 11 12 13 13 13 13 14 14 15 
+15 15 16 17 17 17 19 20 20 20 20 20 22 22 23 23 23 24 24 25 26 26 27 27 28 28 
+28 29 29 30 30 32 33 33 34 35 35 36 37 37 37 38 39 40 40 42 44 44 44 44 44 44 
+45 45 45 46 46 48 48 48 48 48 49 49 49 50 50 50 50
+[4]  82
+\end{verbbox}
+
+\begin{figure}[H]
+    \centering
+    \fbox{
+    \theverbbox
+    }
+    \caption{Example of output file.}
+    \label{output-file-example}
+\end{figure}
+
+The output file gives four essential data, as enumerated below:
+\begin{itemize}
+    \item \textit{[1]}: the original sequence of integers contained in the input file;
+    \item \textit{[2]}: the sequence processed by the sorting algorithm under the memory fault model;
+    \item \textit{[3]}: the sequence sorted correctlty;
+    \item \textit{[4]}: the size of the largest sorted subsequence in [2]. This number can be interpreted as the quality of sorting. As higher, most successful was the sorting operation.
+\end{itemize}
+
+\subsection{Development}
+
+We develop Python scripts to generate input files and analyze our data. To be continued...
+
+\subsection{Data Analysis}
+
+\subsection{Conclusions}

### 2019-12-15 _fabiano/python/05-confidence_intervals_distrib-Z.py
gerados intervalos de confianca

@@ -1,0 +1,106 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+import scipy.stats
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_ler_dados as udata
+
+def mean_confidence_interval(data, confidence):
+    decimais = 4
+
+    prob_inv_cumul = {0.99: 2.576, 0.98: 2.326, 0.95: 1.960, 0.90: 1.645}
+
+    k = prob_inv_cumul[confidence]
+
+    a = 1.0 * np.array(data)
+    n = len(a)
+
+    mean, std_error, std_dev = np.mean(a), scipy.stats.sem(a), np.std(a)
+
+    mean = np.round(mean, decimais)
+    std_error = np.round(std_error, decimais)
+    std_dev = np.round(std_dev, decimais)
+
+    h = k * std_error
+    h = np.round(h, decimais)
+
+    lim_inferior = np.round(mean-h, decimais)
+    lim_superior = np.round(mean+h, decimais)
+
+    return lim_inferior, mean, lim_superior, h, std_error, std_dev
+
+def printInfo(lim_inferior, mean, lim_superior, h, std_error, std_dev):
+    s = '%.4f ≤ µ ≤ %.4f  media=%.4f   h=%.4f    std_error=%.4f    std_dev=%.4f' % (lim_inferior, lim_superior, mean, h, std_error, std_dev)
+    return s
+
+def printCsvInfo(coef_conf, prob, size, alg, coluna, lim_inferior, mean, lim_superior, h, std_error, std_dev):
+    s = '%s;%s;%s;%s;%s;%.4f;%.4f;%.4f;%.4f;%.4f;%.4f\n' % (coluna, coef_conf, prob, size, alg, lim_inferior, mean, lim_superior, std_error, h, std_dev)
+    return s
+
+
+
+path_arq_destino = '../02-Estatisticas/interv_confianca_distrib_z/_intervalos_confianca_distrib_Z.txt'
+if os.path.exists(path_arq_destino):
+    os.remove(path_arq_destino)
+arq_destino = open(path_arq_destino, 'w+')
+
+
+probs = udata.PROBABILIDADES
+sizes = udata.TAMANHOS
+algs  = udata.ALGORTIMOS
+# probs = [0.05]
+# sizes = [100]
+# algs  = ['bubble']
[…]

### 2019-12-15 _fabiano/python/06-confidence_intervals_distrib-T.py

@@ -1,0 +1,115 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+import scipy.stats
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_ler_dados as udata
+
+def mean_confidence_interval_distrib_T(data, confidence):
+    decimais = 4
+
+    # estes são só para N = 1000
+    prob_inv_cumul = {0.99: 2.330, 0.98: 2.056, 0.95: 1.646, 0.90: 1.282}
+
+    k = prob_inv_cumul[confidence]
+
+    a = 1.0 * np.array(data)
+
+    n = len(a)
+    v = n - 1 #calcula o grau de liberdade (letra grega "ni" que parece um "v")
+
+    mean = np.mean(a)
+    std_error = scipy.stats.sem(a)
+
+    var_nao_tendenciosa = np.var(a, ddof=1)
+    std_dev_nao_tendencioso = np.sqrt(var_nao_tendenciosa)
+
+    mean = np.round(mean, decimais)
+    std_error = np.round(std_error, decimais)
+    std_dev = np.round(std_dev_nao_tendencioso, decimais)
+
+    h = k * std_error
+    h = np.round(h, decimais)
+
+    lim_inferior = np.round(mean-h, decimais)
+    lim_superior = np.round(mean+h, decimais)
+
+    # print( lim_inferior, mean, lim_superior, h, std_error, std_dev)
+    return lim_inferior, mean, lim_superior, h, std_error, std_dev
+
+def printInfo(lim_inferior, mean, lim_superior, h, std_error, std_dev):
+    s = '%.4f ≤ µ ≤ %.4f  media=%.4f   h=%.4f    std_error=%.4f    std_dev=%.4f' % (lim_inferior, lim_superior, mean, h, std_error, std_dev)
+    return s
+
+def printCsvInfo(coef_conf, prob, size, alg, coluna, lim_inferior, mean, lim_superior, h, std_error, std_dev):
+    s = '%s;%s;%s;%s;%s;%.4f;%.4f;%.4f;%.4f;%.4f;%.4f\n' % (coluna, coef_conf, prob, size, alg, lim_inferior, mean, lim_superior, std_error, h, std_dev)
+    return s
+
+
+
[…]

### 2019-12-15 _fabiano/python/teste-6-confidence_intervals.py

@@ -1,0 +1,115 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+import scipy.stats
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_ler_dados as udata
+
+def mean_confidence_interval(data, confidence):
+    decimais = 4
+
+    prob_inv_cumul = {0.99: 2.576, 0.98: 2.326, 0.95: 1.960, 0.90: 1.645}
+
+    k = prob_inv_cumul[confidence]
+
+    a = 1.0 * np.array(data)
+    n = len(a)
+
+    mean, std_error, std_dev = np.mean(a), scipy.stats.sem(a), np.std(a)
+
+    mean = np.round(mean, decimais)
+    std_error = np.round(std_error, decimais)
+    std_dev = np.round(std_dev, decimais)
+
+    h = k * std_error
+    h = np.round(h, decimais)
+
+    lim_inferior = np.round(mean-h, decimais)
+    lim_superior = np.round(mean+h, decimais)
+
+    return lim_inferior, mean, lim_superior, h, std_error, std_dev
+
+def printInfo(lim_inferior, mean, lim_superior, h, std_error, std_dev):
+    s = '%.4f ≤ µ ≤ %.4f  media=%.4f   h=%.4f    std_error=%.4f    std_dev=%.4f' % (lim_inferior, lim_superior, mean, h, std_error, std_dev)
+    return s
+
+def printCsvInfo(coef_conf, prob, size, alg, coluna, lim_inferior, mean, lim_superior, h, std_error, std_dev):
+    s = '%s;%s;%s;%s;%s;%.4f;%.4f;%.4f;%.4f;%.4f;%.4f\n' % (coluna, coef_conf, prob, size, alg, lim_inferior, mean, lim_superior, std_error, h, std_dev)
+    return s
+
+
+
+path_arq_destino = '../02-Estatisticas/_confidence_intervals.txt'
+if os.path.exists(path_arq_destino):
+    os.remove(path_arq_destino)
+arq_destino = open(path_arq_destino, 'w+')
+
+
+probs = udata.PROBABILIDADES
+sizes = udata.TAMANHOS
+algs  = udata.ALGORTIMOS
+# probs = [0.05]
+# sizes = [100]
+# algs  = ['bubble']
+
+coeficientes_confianca = [0.99, 0.98, 0.95, 0.90]
+
[…]

### 2019-12-16 _fabiano/python/Teste-7-anova.py
gerados dados e graficos para ANOVA e TESTE DE NORMALIDADE SHAPIRO-WILK

@@ -1,0 +1,132 @@
+import os
+import pandas as pd
+import scipy.stats as stats
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+
+import matplotlib.pyplot as plt
+
+import util_ler_dados as udata
+import util_graficos as graf
+
+path_arq_destino = '../03-Anova'
+
+# def gerarGraficosQQPlot(ind_graf, col_desc, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
+def gerarGraficosQQPlot(ind_graf, ax, col_desc, algoritmo, data):
+
+    ax = plt.subplot(2,2,ind_graf)
+    plt.title('%s - %s' % (algoritmo, col_desc))
+    graf.gerarQQPlot(ax=ax, data=data)
+
+    # ax = plt.subplot(2,2,2)
+    # plt.title('% Desordenados (KDE)')
+    # graf.gerarQQPlot(ax, df_bubble)
+    #
+    # ax = plt.subplot(2,2,3)
+    # plt.title('% Maior Array')
+    # graf.gerarQQPlot(ax, df_bubble)
+    #
+    # ax = plt.subplot(2,2,4)
+    # plt.title('% Maior Array (KDE)')
+    # graf.gerarQQPlot(ax, df_bubble)
+
+
+
+def printShapiroTest(data, desc, arq_destino):
+    W, p_value = stats.shapiro(data)
+    s = '        - %s: W = %0.6f / p_value = %.6f' % (desc, W, p_value)
+    print(s)
+    arq_destino.write(s+'\n')
+    return W, p_value
+
+
+
+def printAnova(col, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
+
+    s = '    * TESTE DE NORMALIDADE (SHAPIRO-WILK):'
+    print(s)
+    arq_destino.write(s+'\n')
+
+    s = '      -----------------------------------'
+    print(s)
+    arq_destino.write(s + '\n')
+
+
+    printShapiroTest(df_bubble[col], 'BUBBLE'.ljust(9), arq_destino)
+    printShapiroTest(df_insertion[col], 'INSERTION'.ljust(9), arq_destino)
+    printShapiroTest(df_merge[col], 'MERGE'.ljust(9), arq_destino)
+    printShapiroTest(df_quick[col], 'QUICK'.ljust(9), arq_destino)
+    print('')
+    arq_destino.write('\n')
+
+    f_statistic, p_value = stats.f_oneway(
[…]

### 2019-12-16 _fabiano/python/lixo.py

@@ -1,0 +1,26 @@
+# QQ Plot
+from numpy.random import seed
+from numpy.random import randn
+from statsmodels.graphics.gofplots import qqplot
+import matplotlib.pyplot as plt
+
+import util_ler_dados as udata
+
+
+# # seed the random number generator
+# seed(1)
+# # generate univariate observations
+# data = 5 * randn(100) + 50
+# # q-q plot
+
+data = udata.obterDados(probs=[0.05], sizes=[100])
+
+fig = plt.figure(figsize=[10, 5])
+plt.suptitle('Titulo')
+ax = plt.gca()
+
+# qqplot(data=data[udata.COLUNA_MAIOR_ARRAY], line='s')
+# qqplot(data=data[udata.COLUNA_DESORDENADOS], line='s')
+# qqplot(data=data[udata.COLUNA_MAIOR_ARRAY_PERCENTUAL], line='s')
+qqplot(ax=ax, data=data[udata.COLUNA_DESORDENADOS_PERCENTUAL], line='s')
+plt.show()

### 2019-12-16 _fabiano/python/util_graficos.py

@@ -8,6 +8,12 @@ import numpy as np
 import pandas as pd
 
 import seaborn as sns
+from statsmodels.graphics.gofplots import qqplot
+
+
+def gerarQQPlot(ax, data, line='s'):
+    fig = qqplot(ax=ax, data=data, line=line)
+    return fig
 
 
 def gerarBarplot(ax, data, x, y, hue, title='', order=None, palette='Blues'):

### 2019-12-16 _fabiano/python/util_ler_dados.py

@@ -18,6 +18,13 @@ TAMANHOS = [100, 1000, 10000]
 
 ALGORTIMOS = ['bubble', 'merge', 'quick', 'insertion']
 
+COLUNAS_DEPENDENTES = ['largest_sorted_subarray','percentual_maior_array','k_unordered_sequence','percentual_k_unordered']
+
+COLUNA_MAIOR_ARRAY = COLUNAS_DEPENDENTES[0]
+COLUNA_MAIOR_ARRAY_PERCENTUAL = COLUNAS_DEPENDENTES[1]
+COLUNA_DESORDENADOS = COLUNAS_DEPENDENTES[2]
+COLUNA_DESORDENADOS_PERCENTUAL = COLUNAS_DEPENDENTES[3]
+
 def obterDados(probs = [0.01, 0.02, 0.05, 0.001, 0.0001], sizes=[100, 1000, 10000]):
     pasta_origem = '../data/data_grouped'
     arq_metadata = open('%s/_metadata.csv' % (pasta_origem), 'w+')
@@ -49,6 +56,7 @@ def filtrarPorAlgoritmo(df, algoritmo):
 
 def filtrarPorTamanhoArray(df, tamanho):
     return df[df['size_of_array'] == tamanho]
+
 
 def obterEstatisticasPorTamanho_Algoritmo(df):
     df_means = df.groupby(['size_of_array', 'algoritmo']).mean()

### 2019-12-17 _fabiano/python/01-CreateDatasetFromData-2.py
dados normalizados para Perc. Desordenados. Gerados os graficos e teste de normalidade

@@ -1,0 +1,94 @@
+import sys
+import os
+import shutil
+import datetime
+import time
+
+
+def calcular_k_unordered_sequence(data):
+    arr = data.split(' ')
+    #
+    indice1 = 0
+    indice2 = 1
+    indice_max = len(arr) - 1
+    k = 0
+    #
+    while (indice1 < indice_max):
+        #
+        if (int(arr[indice1]) > int(arr[indice2])):
+            k += 1
+        #
+        indice1 += 1
+        indice2 += 1
+    #
+    return k
+
+def main(algoritmo, data_size, prob_erro, ind_arq, arq_destino):
+    ind_arq = ('0%s' % (ind_arq))[-2:]
+    d_size = ('00000%s' % (data_size))[-5:]
+
+    outFile = 'data-out-%.4f-%s-%s-%s.txt' % (prob_erro, d_size, algoritmo, ind_arq)
+
+    if os.path.exists('data-out-2/%s'%outFile):
+        print('        %s'%outFile)
+
+        # le o arquivo .OUT
+        file = open('data-out-2/%s'%outFile, 'r')
+        # obtem os dados de cada uma das 4 linhas
+        lines = file.readlines()
+        l1_original_array = lines[0]
+        l2_sorting_with_fault = lines[1]
+        l3_sorting_ok = lines[2]
+        l4_largest_sorted_subarray = int(lines[3])
+
+        # se for a prob. erro default (1/n) ajusta a descricao no arquivo
+        prob_erro_csv = prob_erro
+
+        # calcula o percentual do maior array
+        percentual_maior_array = 100.0 * int(l4_largest_sorted_subarray) / int(data_size)
+
+        #
+        k_unordered_sequence = calcular_k_unordered_sequence(l2_sorting_with_fault)
+        #
+        percentual_k_unordered = 100.0 * int(k_unordered_sequence) / int(data_size)
+        #
+        arq_destino.write('%s;%s;%s;%s;%s;%.2f;%.2f\n' % (
+        algoritmo, prob_erro_csv, data_size, l4_largest_sorted_subarray, k_unordered_sequence, percentual_k_unordered,
+        percentual_maior_array))
+
+
+# define as pastas contendo os dados
+pasta_origem = 'data-out-2'
+pastas = os.listdir(pasta_origem)
+
+#abre o arquivo onde serao salvos os dados extraidos
[…]

### 2019-12-17 _fabiano/python/01-CreateDatasetFromData.py

@@ -23,76 +23,146 @@ def calcular_k_unordered_sequence(data):
     #
     return k
 
+def main(algoritmo, data_size, prob_erro, ind_arq, arq_destino):
+    ind_arq = ('0%s' % (ind_arq))[-2:]
+    d_size = ('00000%s' % (data_size))[-5:]
+
+    outFile = 'data-out-%.4f-%s-%s-%s.txt' % (prob_erro, d_size, algoritmo, ind_arq)
+
+    if os.path.exists('data-out/%s'%outFile):
+        print('        %s'%outFile)
+
+        # le o arquivo .OUT
+        file = open('data-out/%s'%outFile, 'r')
+        # obtem os dados de cada uma das 4 linhas
+        lines = file.readlines()
+        l1_original_array = lines[0]
+        l2_sorting_with_fault = lines[1]
+        l3_sorting_ok = lines[2]
+        l4_largest_sorted_subarray = int(lines[3])
+
+        # se for a prob. erro default (1/n) ajusta a descricao no arquivo
+        prob_erro_csv = prob_erro
+        # if (prob_erro == '1/n'):
+        #     prob_erro_csv = '%g' % (1.0 / int(n))
+
+        # calcula o percentual do maior array
+        percentual_maior_array = 100.0 * int(l4_largest_sorted_subarray) / int(data_size)
+
+        #
+        k_unordered_sequence = calcular_k_unordered_sequence(l2_sorting_with_fault)
+        #
+        percentual_k_unordered = 100.0 * int(k_unordered_sequence) / int(data_size)
+        #
+        arq_destino.write('%s;%s;%s;%s;%s;%.2f;%.2f\n' % (
+        algoritmo, prob_erro_csv, data_size, l4_largest_sorted_subarray, k_unordered_sequence, percentual_k_unordered,
+        percentual_maior_array))
 
 
 # define as pastas contendo os dados
-pasta_origem = '../../../../data'
+pasta_origem = 'data-out'
 pastas = os.listdir(pasta_origem)
 
 #abre o arquivo onde serao salvos os dados extraidos
 #se o arquivo ja existir, entao apaga e cria novamente
-path_arq_destino = '%s/_dados_extraidos.csv'%pasta_origem
+path_arq_destino = 'data-csv/dados_extraidos.csv'
 if os.path.exists(path_arq_destino):
     os.remove(path_arq_destino)
 
[…]

### 2019-12-17 _fabiano/python/02-NOVO-2-Medias_por_algoritmo_e_prob_erro.py

@@ -1,0 +1,186 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+import util_ler_dados as udata
+
+# %matplotlib inline
+
+# ========================================================
+# estilos de graficos :
+# >>  https://tonysyu.github.io/raw_content/matplotlib-style-gallery/gallery.html
+# ========================================================
+# plt.style.use('seaborn-whitegrid')
+# plt.style.use('seaborn-pastel')
+# plt.style.use('seaborn-colorblind')
+# plt.style.use('seaborn-bright')
+# plt.style.use('grayscale')
+# plt.style.use('ggplot')
+# plt.style.use('fivethirtyeight')
+# plt.style.use('dark_background')
+# plt.style.use('classic')
+# plt.style.use('bmh')
+
+
+
+# pasta_origem = 'data-2/data_grouped'
+# arq_metadata = open('%s/_metadata.csv' % (pasta_origem), 'w+')
+
+probs = ['0.01','0.02','0.05']
+# probs = ['0.01']#,'0.02']#,'0.05','0.001','0.0001']
+
+sizes = ['100','1000','10000']
+
+df_tudo = udata.obterDados2()
+
+#ordena os registros por algoritmo
+df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+
+# gera os graficos
+rows = 5
+cols = 2
+
+larg_fig = 32
+alt_fig  = 41
+font_size = 15
+
+sns_palette = 'Set2'
+color_map = sns.color_palette(sns_palette, n_colors=4)
+
+gerar_graficos = True
+gerar_csvs_com_dados_dos_graficos = True
+
+df_dados_csv = pd.DataFrame()
+
+for prob in probs:
+    data = df_tudo[df_tudo.probabilidade_erro == float(prob)]
+
+    df_means = data.groupby(['size_of_array', 'algoritmo']).mean()
+    df_std = data.groupby(['size_of_array', 'algoritmo']).std()
+    df_min = data.groupby(['size_of_array', 'algoritmo']).min()
+    df_max = data.groupby(['size_of_array', 'algoritmo']).max()
+
[…]

### 2019-12-17 _fabiano/python/04-NOVO-2-Distribuicao_das_medidas_escolhidas.py

@@ -1,0 +1,173 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+
+pasta_origem = '../data/data_grouped'
+
+alg = ['quick','bubble','merge','insertion']
+probs = [0.02,0.05]
+sizes = [100,1000,10000]
+
+
+alg = ['quick','merge']
+alg = ['quick']
+probs = [0.01]
+sizes = [100]
+
+
+csv = 'data-csv-2/dados_extraidos-2.csv'
+df_tudo = pd.read_csv(delimiter = ';', filepath_or_buffer = csv)
+print(df_tudo)
+
+#ordena os registros por algoritmo
+df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+
+
+# gera os graficos
+rows = 5
+cols = 2
+
+larg_fig = 32
+alt_fig  = 41
+font_size = 15
+
+sns_palette = 'Set2'
+color_map = sns.color_palette(sns_palette, n_colors=4)
+
+gerar_graficos = True
+gerar_csvs_com_dados_dos_graficos = True
+
+df_dados_csv = pd.DataFrame()
+
+for prob in probs:
+    data = df_tudo[df_tudo.probabilidade_erro == float(prob)]
+
+    group_by = ['probabilidade_erro', 'algoritmo']
+    df_means = data.groupby(group_by).mean()
+    df_std = data.groupby(group_by).std()
+    df_min = data.groupby(group_by).min()
+    df_max = data.groupby(group_by).max()
+
+    # colunas_join = ['largest_sorted_subarray','k_unordered_sequence','percentual_k_unordered','percentual_maior_array']
+    colunas_join = ['percentual_k_unordered','percentual_maior_array']
+    df_dados_csv = df_means[colunas_join]
+    df_dados_csv = df_dados_csv.join(other=df_std[colunas_join], rsuffix='_std')
+    df_dados_csv = df_dados_csv.join(other=df_min[colunas_join], rsuffix='_min')
+    df_dados_csv = df_dados_csv.join(other=df_max[colunas_join], rsuffix='_max', lsuffix='_mean')
+
+    indx = 1
+
+    #se tiver dados no DF
[…]

### 2019-12-17 _fabiano/python/04-NOVO-Distribuicao_das_medidas_escolhidas.py

@@ -1,0 +1,193 @@
+#imports
+import os
+
+import matplotlib.pyplot as plt
+import matplotlib.font_manager as font_manager
+
+import numpy as np
+import pandas as pd
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+import util_graficos as graf
+
+pasta_origem = '../data/data_grouped'
+
+alg = [
+    'quick',
+    'bubble',
+    'merge',
+    'insertion'
+    ]
+
+probs = [
+    0.0100,
+    0.0010,
+    0.0001,
+]
+
+sizes = [
+    100,
+    1000,
+    10000
+    ]
+
+csv = 'data-csv/dados_extraidos.csv'
+df_tudo = pd.read_csv(delimiter = ';', filepath_or_buffer = csv)
+
+# #le os arquivos de entrada
+# for prob in probs:
+#     for size in sizes:
+#         filtro_arq = '%s_%s_' % (prob, size)
+#
+#         arqs_in = os.listdir(pasta_origem)
+#         for f in arqs_in:
+#             if (f.startswith(filtro_arq)):
+#                 print(f)
+#                 csv = os.path.join(pasta_origem, f)
+#                 df_temp = pd.read_csv(delimiter = ';', filepath_or_buffer = csv)
+#                 df_tudo = df_tudo.append(df_temp)
+
+#ordena os registros por algoritmo
+df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+
+
+# gera os graficos
+rows = 5
+cols = 2
+
+larg_fig = 32
+alt_fig  = 41
+font_size = 15
+
+sns_palette = 'Set2'
+color_map = sns.color_palette(sns_palette, n_colors=4)
+
+gerar_graficos = True
+gerar_csvs_com_dados_dos_graficos = True
+
+df_dados_csv = pd.DataFrame()
+
+for prob in probs:
+    data = df_tudo[df_tudo.probabilidade_erro == float(prob)]
+
+    group_by = ['probabilidade_erro', 'algoritmo']
+    df_means = data.groupby(group_by).mean()
+    df_std = data.groupby(group_by).std()
+    df_min = data.groupby(group_by).min()
+    df_max = data.groupby(group_by).max()
+
+    # colunas_join = ['largest_sorted_subarray','k_unordered_sequence','percentual_k_unordered','percentual_maior_array']
[…]

### 2019-12-17 _fabiano/python/Teste-7-NOVO-2-anova.py

@@ -1,0 +1,182 @@
+import os
+import pandas as pd
+import scipy.stats as stats
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+
+import matplotlib.pyplot as plt
+
+import util_ler_dados as udata
+import util_graficos as graf
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+path_arq_destino = '03-Anova-2'
+
+# def gerarGraficosQQPlot(ind_graf, col_desc, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
+def gerarGraficosQQPlot(ind_graf, ax, col_desc, algoritmo, data):
+
+    ax = plt.subplot(2,2,ind_graf)
+    plt.title('%s - %s' % (algoritmo, col_desc))
+    graf.gerarQQPlot(ax=ax, data=data)
+
+
+def gerarGraficosBoxPlot(ax, col, col_desc, dfs):
+    data = pd.DataFrame()
+    for df in dfs:
+        data = data.append(other=df)
+
+    plt.title('%s' % (col_desc))
+    sns.boxplot(data=data, x='algoritmo', y=col, ax=ax)
+
+
+
+
+def printShapiroTest(data, desc, arq_destino):
+    W, p_value = stats.shapiro(data)
+    s = '        - %s: W = %0.6f / p_value = %.6f' % (desc, W, p_value)
+    print(s)
+    arq_destino.write(s+'\n')
+    return W, p_value
+
+
+
+def printAnova(col, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
+
+    s = '    * TESTE DE NORMALIDADE (SHAPIRO-WILK):'
+    print(s)
+    arq_destino.write(s+'\n')
+
+    s = '      -----------------------------------'
+    print(s)
+    arq_destino.write(s + '\n')
+
+
+    printShapiroTest(df_bubble[col], 'BUBBLE'.ljust(9), arq_destino)
+    printShapiroTest(df_insertion[col], 'INSERTION'.ljust(9), arq_destino)
+    printShapiroTest(df_merge[col], 'MERGE'.ljust(9), arq_destino)
+    printShapiroTest(df_quick[col], 'QUICK'.ljust(9), arq_destino)
+    print('')
+    arq_destino.write('\n')
+
+    f_statistic, p_value = stats.f_oneway(
+                                          df_bubble[col],
+                                          df_insertion[col],
+                                          df_merge[col],
[…]

### 2019-12-17 _fabiano/python/Teste-7-NOVO-anova.py

@@ -1,0 +1,182 @@
+import os
+import pandas as pd
+import scipy.stats as stats
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+
+import matplotlib.pyplot as plt
+
+import util_ler_dados as udata
+import util_graficos as graf
+
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
+path_arq_destino = '03-Anova'
+
+# def gerarGraficosQQPlot(ind_graf, col_desc, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
+def gerarGraficosQQPlot(ind_graf, ax, col_desc, algoritmo, data):
+
+    ax = plt.subplot(2,2,ind_graf)
+    plt.title('%s - %s' % (algoritmo, col_desc))
+    graf.gerarQQPlot(ax=ax, data=data)
+
+
+def gerarGraficosBoxPlot(ax, col, col_desc, dfs):
+    data = pd.DataFrame()
+    for df in dfs:
+        data = data.append(other=df)
+
+    plt.title('%s' % (col_desc))
+    sns.boxplot(data=data, x='algoritmo', y=col, ax=ax)
+
+
+
+
+def printShapiroTest(data, desc, arq_destino):
+    W, p_value = stats.shapiro(data)
+    s = '        - %s: W = %0.6f / p_value = %.6f' % (desc, W, p_value)
+    print(s)
+    arq_destino.write(s+'\n')
+    return W, p_value
+
+
+
+def printAnova(col, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
+
+    s = '    * TESTE DE NORMALIDADE (SHAPIRO-WILK):'
+    print(s)
+    arq_destino.write(s+'\n')
+
+    s = '      -----------------------------------'
+    print(s)
+    arq_destino.write(s + '\n')
+
+
+    printShapiroTest(df_bubble[col], 'BUBBLE'.ljust(9), arq_destino)
+    printShapiroTest(df_insertion[col], 'INSERTION'.ljust(9), arq_destino)
+    printShapiroTest(df_merge[col], 'MERGE'.ljust(9), arq_destino)
+    printShapiroTest(df_quick[col], 'QUICK'.ljust(9), arq_destino)
+    print('')
+    arq_destino.write('\n')
+
+    f_statistic, p_value = stats.f_oneway(
+                                          df_bubble[col],
+                                          df_insertion[col],
+                                          df_merge[col],
[…]

### 2019-12-17 _fabiano/python/Teste-7-anova.py

@@ -9,6 +9,9 @@ import matplotlib.pyplot as plt
 import util_ler_dados as udata
 import util_graficos as graf
 
+import seaborn as sns
+plt.style.use('seaborn-whitegrid')
+
 path_arq_destino = '../03-Anova'
 
 # def gerarGraficosQQPlot(ind_graf, col_desc, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
@@ -18,17 +21,15 @@ def gerarGraficosQQPlot(ind_graf, ax, col_desc, algoritmo, data):
     plt.title('%s - %s' % (algoritmo, col_desc))
     graf.gerarQQPlot(ax=ax, data=data)
 
-    # ax = plt.subplot(2,2,2)
-    # plt.title('% Desordenados (KDE)')
-    # graf.gerarQQPlot(ax, df_bubble)
-    #
-    # ax = plt.subplot(2,2,3)
-    # plt.title('% Maior Array')
-    # graf.gerarQQPlot(ax, df_bubble)
-    #
-    # ax = plt.subplot(2,2,4)
-    # plt.title('% Maior Array (KDE)')
-    # graf.gerarQQPlot(ax, df_bubble)
+
+def gerarGraficosBoxPlot(ax, col, col_desc, dfs):
+    data = pd.DataFrame()
+    for df in dfs:
+        data = data.append(other=df)
+
+    plt.title('%s' % (col_desc))
+    sns.boxplot(data=data, x='algoritmo', y=col, ax=ax)
+
 
 
 
@@ -78,6 +79,13 @@ def printAnova(col, df_bubble, df_insertion, df_merge, df_quick, arq_destino):
     arq_destino.write(s+'\n')
 
 
+
+colunas_desc={'largest_sorted_subarray':'maior_array',
+              'percentual_maior_array':'maior_array_percentual',
+              'k_unordered_sequence':'desordenados',
+              'percentual_k_unordered':'desordenados_percentual'}
+
+
 for prob in udata.PROBABILIDADES:
     for size in udata.TAMANHOS:
         df = udata.obterDados(probs=[prob], sizes=[size])
@@ -90,16 +98,35 @@ for prob in udata.PROBABILIDADES:
                 os.remove(arq_destino)
             arq_destino = open(arq_destino, 'w+')
 
-            df_bubble = df[df['algoritmo'] == 'bubble']
-            df_merge = df[df['algoritmo'] == 'merge']
[…]

### 2019-12-17 _fabiano/python/gen_2.py

@@ -1,0 +1,25 @@
+from random import *
+
+n_sizes = [100, 1000, 10000]
+epss = [ 0.02, 0.05 ]
+
+n_sizes = [100]
+epss = [ 0.01 ]
+
+for eps in epss:
+    for n in n_sizes:
+        for c in range(1,31):
+            eps = eps
+            maxr = n/2
+            s1 = ('0%s'%(c))[-2:]
+            s2 = str(eps).rjust(5)
+            s3 = ('00000%s' % (n))[-5:]
+
+            arq = "data-in-2/data-in-%.4f-%s-%s.txt"%(eps, s3, s1)
+            print(arq)
+            f = open(arq,"w")
+            f.write(str(eps) + " " + str(n))
+            for i in range(n):
+                f.write(" " + str(randint(1,maxr)))
+            f.write("\n")
+            f.close()

### 2019-12-17 _fabiano/python/main_execution_2.py

@@ -1,0 +1,40 @@
+import sys
+import os
+
+
+def main(sorting_alg, data_size, perc_rate, ind_arq):
+    ind_arq = ('0%s' % (ind_arq))[-2:]
+    d_size = ('00000%s' % (data_size))[-5:]
+
+    inFile = 'data-in-%.4f-%s-%s.txt' % (perc_rate, d_size, ind_arq)
+    if os.path.exists('data-in-2/%s'%inFile):
+        print('        %s'%inFile)
+
+        outFile = 'data-out-%.4f-%s-%s-%s.txt'%(perc_rate, d_size, sorting_alg, ind_arq)
+        cmd = './%s < data-in-2/%s > data-out-2/%s' % (sorting_alg, inFile, outFile)
+        # print(cmd)
+        os.system(cmd)
+
+
+alg = ['quick', 'bubble', 'merge', 'insertion']
+perc_rates = [0.02, 0.05]
+d_size = [100, 1000, 10000]
+
+alg = ['quick', 'merge']
+alg = [ 'quick']
+perc_rates = [0.01]
+d_size = [100]
+
+repetitions = 30
+
+print('Iniciando execucao...')
+for a in alg:
+    print('Algoritmo: ' + a)
+    for prob in perc_rates:
+        print('  Perc. Rate: %s' % prob)
+        for size in d_size:
+            print('    Data Size: %s' % size)
+            for ind_arq in range(1, 31):
+                main(a, size, prob, ind_arq)
+
+print('Finalizando execucao...')

### 2019-12-17 _fabiano/python/util_ler_dados.py

@@ -25,24 +25,31 @@ COLUNA_MAIOR_ARRAY_PERCENTUAL = COLUNAS_DEPENDENTES[1]
 COLUNA_DESORDENADOS = COLUNAS_DEPENDENTES[2]
 COLUNA_DESORDENADOS_PERCENTUAL = COLUNAS_DEPENDENTES[3]
 
-def obterDados(probs = [0.01, 0.02, 0.05, 0.001, 0.0001], sizes=[100, 1000, 10000]):
-    pasta_origem = '../data/data_grouped'
-    arq_metadata = open('%s/_metadata.csv' % (pasta_origem), 'w+')
-
-    df_tudo = pd.DataFrame()
-
-    for prob in probs:
-        for size in sizes:
-            filtro_arq = '%s_%s_' % (prob, size)
-
-            arqs_in = os.listdir(pasta_origem)
-            for f in arqs_in:
-                if (f.startswith(filtro_arq)):
-                    # print(filtro_arq)
-                    csv = os.path.join(pasta_origem, f)
-                    df_tudo = df_tudo.append( pd.read_csv(delimiter=';', filepath_or_buffer=csv) )
-
+def obterDados2():
+    csv = 'data-csv-2/dados_extraidos-2.csv'
+    df_tudo = pd.read_csv(delimiter=';', filepath_or_buffer=csv)
     return df_tudo
+
+def obterDados():
+    csv = 'data-csv/dados_extraidos.csv'
+    df_tudo = pd.read_csv(delimiter=';', filepath_or_buffer=csv)
+    return df_tudo
+
+    # pasta_origem = 'data-csv'
+    # df_tudo = pd.DataFrame()
+    #
+    # for prob in probs:
+    #     for size in sizes:
+    #         filtro_arq = '%s_%s_' % (prob, size)
+    #
+    #         arqs_in = os.listdir(pasta_origem)
+    #         for f in arqs_in:
+    #             if (f.startswith(filtro_arq)):
+    #                 # print(filtro_arq)
+    #                 csv = os.path.join(pasta_origem, f)
+    #                 df_tudo = df_tudo.append( pd.read_csv(delimiter=';', filepath_or_buffer=csv) )
+    #
+    # return df_tudo
 
 
 def filtrarPorProbabilidadeErro(df, prob):

### 2019-12-17 paper/MaterialsAndMethods.tex
avanços na escrirta

@@
 The content of memory location can change unexpectedly, i.e., faults may happen at any time.
-Considering this, the main objective of this work is to design experiments to answer the following research question:
-
-\begin{itemize}
-    \item \textit{RQ1:} How are sorting algorithms affected by memory faults?
-\end{itemize}
+Considering this, the main objective of this work is to design experiments to answer the following question: \textit{How are sorting algorithms affected by memory faults?}
 
@@
 
-\begin{table}[htbp]
+\begin{table}[H]
     \caption{Dependent and independent variables.}
@@
 
-\begin{figure}[hbtp]
+\begin{figure}[H]
     \centering
@@
     \caption{Example of input file.}
-    \label{input-file-example}
+    \label{fig-input-file-example}
 \end{figure}
 
-The input data shown in the Figure \ref{input-file-example} is divided as follows:
+The input data shown in the Figure \ref{fig-input-file-example} is divided as follows:
 
@@
 Then, we generate 4000 outputs for each combination of sequence size, and the probability of failure, totalizing 36000 files.
-Figure \ref{output-file-example} shows an output file.
+Figure \ref{fig-output-file-example} shows an output file.
 
@@
     \caption{Example of output file.}
-    \label{output-file-example}
+    \label{fig-output-file-example}
 \end{figure}
@@
 
-We develop Python scripts to generate input files and analyze our data. To be continued...
+We develop Python scripts to generate our dataset.
+First, we generate all input files through a given script called \textit{gen.py}.
+This script considers sequence size and the probability of failure to create a sequence of integers.
+Were produced nine input files like Figure \ref{fig-input-file-example}, combining the sequence size and probability of failure listed in Table \ref{table-input-data}.
+
+After that, we developed a script called \textit{main\_execution.py} that is responsible for creating output files based on the input files exposed before.
+At this time, for every input showed in Table \ref{table-input-data} we ran 1000 times to minimize any deviation on the quality of sorting indicator (line \textit{[4]} on Figure \ref{fig-output-file-example}).
+
+As said before, after the execution of this algorithm, 4000 outputs for each combination of sequence size, and the probability of failure, totalizing 36000 files.
+
+To be continued...
 
@@
 
+In this section, we describe our data and the statistic tests used to test the hypothesis showed before.
+
+\subsubsection{Exploratory Data Analysis (EDA)}
+
+Based on the output files generated before, we produce the ...
+
 \subsection{Conclusions}

### 2019-12-18 _fabiano/python/09-NOVO-2-Gerar TABELA ANOVA.py
gerados Dados ANOVA no arquivo ANOVA_TODAS_ANALISES.txt

@@ -1,0 +1,58 @@
+# import plotly.plotly as py
+# import plotly.graph_objs as go
+# from plotly.tools import FigureFactory as FF
+import os
+import sys
+import numpy as np
+import pandas as pd
+import scipy
+import scipy.stats as stats
+
+import statsmodels
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+import util_ler_dados as udata
+
+
+df_tudo = udata.obterDados2()
+
+arq_destino = '03-Anova-2/_ANOVA_TODAS_ANALISES.txt'
+if os.path.exists(arq_destino):
+    os.remove(arq_destino)
+arq_destino = open(arq_destino, 'w+')
+
+for prob in udata.PROBABILIDADES_2:
+    for tam in udata.TAMANHOS:
+        data = udata.obterDfPorProbTam2(prob=prob, tam=tam, df=df_tudo)
+        # print(data.head())
+
+        moore_lm = ols(formula='percentual_k_unordered ~ algoritmo',data=data).fit()
+        anova = sm.stats.anova_lm(moore_lm, typ=2) # Type 2 ANOVA DataFrame
+
+        tit = ' ANOVA para Probabilidade = %s e Tamanho = %s' % (prob, tam)
+        hr = '=' * 60 #len(tit)
+        anov = anova.head(10)
+
+        s = '%s\n%s\n%s\n%s\n\n' %(hr,tit,hr,anov)
+        arq_destino.write(s)
+        print(s)
+
+        #insere dados do Tete de Nomelidade
+        s = '    * TESTE DE NORMALIDADE (SHAPIRO-WILK):\n'
+        s += '      %s\n' % ('-' * (len(s)+6))
+        for alg in udata.ALGORTIMOS:
+            d = data[data['algoritmo'] == alg]['percentual_k_unordered']
+            W, p_value = stats.shapiro(d)
+            s += '        - %s: W = %0.6f / p_value = %.6f \n' % (alg.ljust(9), W, p_value)
+        s += '\n'
+        arq_destino.write(s)
+        print(s)
+
+
+#fecha arquivo
+arq_destino.close()
+
+
+# pr_f = anova['PR(>F)'].values[0]
+# print( '%s  /  %.55f' % (pr_f, pr_f) )
+

### 2019-12-18 _fabiano/python/10-NOVO-2-Gerar TABELA ANOVA por Probabilidades de um mesmo Algoritmo.py

@@ -1,0 +1,63 @@
+# import plotly.plotly as py
+# import plotly.graph_objs as go
+# from plotly.tools import FigureFactory as FF
+import os
+import sys
+import numpy as np
+import pandas as pd
+import scipy
+import scipy.stats as stats
+
+import statsmodels
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+import util_ler_dados as udata
+
+
+df_tudo = udata.obterDados2()
+
+arq_destino = '03-Anova-2/_ANOVA_ANALISES_Probabilidades_de_um_mesmo_Algoritmo.txt'
+if os.path.exists(arq_destino):
+    os.remove(arq_destino)
+arq_destino = open(arq_destino, 'w+')
+
+for alg in udata.ALGORTIMOS:
+    data = udata.filtrarPorAlgoritmo(df=df_tudo, algoritmo=alg)
+    # print(data.head())
+    print(data['probabilidade_erro'].unique())
+
+    moore_lm = ols(formula='percentual_k_unordered ~ probabilidade_erro',data=data).fit()
+    anova = sm.stats.anova_lm(moore_lm, typ=2) # Type 2 ANOVA DataFrame
+
+    tit = ' ANOVA para %s' % (alg.upper())
+    hr = '=' * 70 #len(tit)
+    anov = anova.head(10)
+
+    s = '%s\n%s\n%s\n%s\n\n' %(hr,tit,hr,anov)
+    arq_destino.write(s)
+    print(s)
+
+    #insere dados do Tete de Nomelidade
+    s = '    * TESTE DE NORMALIDADE (SHAPIRO-WILK):\n'
+    s += '      %s\n' % ('-' * (len(s)+6))
+    d = data['percentual_k_unordered']
+    W, p_value = stats.shapiro(d)
+    s += '        - Todas as Probabilidades %s: W = %0.6f / p_value = %.6f \n' % (d.shape[0], W, p_value)
+    s += '\n'
+    arq_destino.write(s)
+    print(s)
+
+    # #insere dados do Tete de Nomelidade
+    # s = '    * TESTE DE NORMALIDADE (SHAPIRO-WILK):\n'
+    # s += '      %s\n' % ('-' * (len(s)+6))
+    # for prob in udata.PROBABILIDADES_2:
+    #     d = data[data['probabilidade_erro'] == prob]['percentual_k_unordered']
+    #     W, p_value = stats.shapiro(d)
[…]

### 2019-12-18 _fabiano/python/Teste-8-Gerar TABELA ANOVA.py

@@ -1,0 +1,58 @@
+# import plotly.plotly as py
+# import plotly.graph_objs as go
+# from plotly.tools import FigureFactory as FF
+import os
+import sys
+import numpy as np
+import pandas as pd
+import scipy
+import scipy.stats as stats
+
+import statsmodels
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+import util_ler_dados as udata
+
+
+df_tudo = udata.obterDados2()
+
+arq_destino = '03-Anova-2/ANOVA_TODAS_ANALISES.txt'
+if os.path.exists(arq_destino):
+    os.remove(arq_destino)
+arq_destino = open(arq_destino, 'w+')
+
+for prob in udata.PROBABILIDADES_2:
+    for tam in udata.TAMANHOS:
+        data = udata.obterDfPorProbTam2(prob=prob, tam=tam, df=df_tudo)
+        # print(data.head())
+
+        moore_lm = ols(formula='percentual_k_unordered ~ algoritmo',data=data).fit()
+        anova = sm.stats.anova_lm(moore_lm, typ=2) # Type 2 ANOVA DataFrame
+
+        tit = ' ANOVA para Probabilidade = %s e Tamanho = %s' % (prob, tam)
+        hr = '=' * 60 #len(tit)
+        anov = anova.head(10)
+
+        s = '%s\n%s\n%s\n%s\n\n' %(hr,tit,hr,anov)
+        arq_destino.write(s)
+        print(s)
+
+        #insere dados do Tete de Nomelidade
+        s = '    * TESTE DE NORMALIDADE (SHAPIRO-WILK):\n'
+        s += '      %s\n' % ('-' * (len(s)+6))
+        for alg in udata.ALGORTIMOS:
+            d = data[data['algoritmo'] == alg]['percentual_k_unordered']
+            W, p_value = stats.shapiro(d)
+            s += '        - %s: W = %0.6f / p_value = %.6f \n' % (alg.ljust(9), W, p_value)
+        s += '\n'
+        arq_destino.write(s)
+        print(s)
+
+
+#fecha arquivo
+arq_destino.close()
+
+
+# pr_f = anova['PR(>F)'].values[0]
+# print( '%s  /  %.55f' % (pr_f, pr_f) )
+

### 2019-12-18 _fabiano/python/util_ler_dados.py

@@ -1,4 +1,4 @@
-#imports
+# imports
 import os
 
 import matplotlib.pyplot as plt
@@ -8,27 +8,32 @@ import numpy as np
 import pandas as pd
 
 import seaborn as sns
+
 plt.style.use('seaborn-whitegrid')
 
 import util_graficos as graf
 
 PROBABILIDADES = ['0.01', '0.02', '0.05', '0.001', '0.0001']
+PROBABILIDADES_2 = [0.01, 0.02, 0.05]
 
 TAMANHOS = [100, 1000, 10000]
 
 ALGORTIMOS = ['bubble', 'merge', 'quick', 'insertion']
 
-COLUNAS_DEPENDENTES = ['largest_sorted_subarray','percentual_maior_array','k_unordered_sequence','percentual_k_unordered']
+COLUNAS_DEPENDENTES = ['largest_sorted_subarray', 'percentual_maior_array', 'k_unordered_sequence',
+                       'percentual_k_unordered']
 
 COLUNA_MAIOR_ARRAY = COLUNAS_DEPENDENTES[0]
 COLUNA_MAIOR_ARRAY_PERCENTUAL = COLUNAS_DEPENDENTES[1]
 COLUNA_DESORDENADOS = COLUNAS_DEPENDENTES[2]
 COLUNA_DESORDENADOS_PERCENTUAL = COLUNAS_DEPENDENTES[3]
 
+
 def obterDados2():
     csv = 'data-csv-2/dados_extraidos-2.csv'
     df_tudo = pd.read_csv(delimiter=';', filepath_or_buffer=csv)
     return df_tudo
+
 
 def obterDados():
     csv = 'data-csv/dados_extraidos.csv'
@@ -58,8 +63,10 @@ def filtrarPorProbabilidadeErro(df, prob):
 
     return df[df.probabilidade_erro == prob]
 
+
 def filtrarPorAlgoritmo(df, algoritmo):
     return df[df.algoritmo == algoritmo]
+
 
 def filtrarPorTamanhoArray(df, tamanho):
     return df[df['size_of_array'] == tamanho]
@@ -72,3 +79,22 @@ def obterEstatisticasPorTamanho_Algoritmo(df):
     df_max = df.groupby(['size_of_array', 'algoritmo']).max()
     df_var = df.groupby(['size_of_array', 'algoritmo']).var()
     return df_means, df_std, df_min, df_max, df_var
+
+
[…]

### 2019-12-18 paper/MaterialsAndMethods.tex
adicao de imagens e continuacao da escrita

@@
 
-To be continued...
+\textcolor{red}{To be continued...}
 
@@
 
-Based on the output files generated before, we produce the ...
+Based on the output files generated before, our starting point was to test if the dataset had a normal distribution.
+To achieve this, we use Shapiro-Wilk normality test.
+After we run these tests, only the distribution related to the dependent variable \textit{unordered elements size} was considered normal.
+Figure \ref{fig-distribution-graph} shows an example of this distribution.
+In these graphs, the red vertical line means the mean, and the blue vertical line means the median.
+The distributions were normal in all combinations of independent variables for dependent variable \textit{unordered elements size}.
+
+\begin{figure}[H]
+    \centering
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Bubble_distribution_graph}}
+     \textsf{\caption[Distribution Graph for bubblesort.]{Distribution Graph for bubblesort.\label{fig-dist-bubble-001-100}}}
+     \end{subfigure}%
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Insertion_distribution_graph.png}}
+     \textsf{\caption[Distribution Graph for insertion sort.]{Distribution Graph for insertion sort.\label{fig-dist-insertion-001-100}}}
+     \end{subfigure}
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Merge_distribution_graph.png}}
+     \textsf{\caption[Distribution Graph for mergesort.]{Distribution Graph for mergesort.\label{fig-dist-merge-001-100}}}
+     \end{subfigure}%
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Quick_distribution_graph.png}}
+     \textsf{\caption[Distribution Graph for quicksort.]{Distribution Graph for quicksort.\label{fig-dist-quick-001-100}}}
+     \end{subfigure}
+     \caption{Distribution graph for a probability failure of 1\% and a sequence size of 10000.}
+    \label{fig-distribution-graph}
+\end{figure}
+
+Q-Q plot shows that how much more blue points close to the red line, most normal is the distribution.
+Figure \ref{fig-qqplot} below presents this graph for a probability failure of 1\% and a sequence size of 10000 for considered sorting algorithms.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.37]{figures/anova_prob_0_01_tam_10000_DESORDENADOS_PERCENTUAL.png}
+    \textsf{\caption[Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.]{Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.\label{fig-qqplot}}}
+ \end{figure}
 

### 2019-12-18 _fabiano/python/09-NOVO-2-Gerar TABELA ANOVA.py
gerado Anova com Interacoes

@@ -26,8 +26,8 @@ for prob in udata.PROBABILIDADES_2:
         data = udata.obterDfPorProbTam2(prob=prob, tam=tam, df=df_tudo)
         # print(data.head())
 
-        moore_lm = ols(formula='percentual_k_unordered ~ algoritmo',data=data).fit()
-        anova = sm.stats.anova_lm(moore_lm, typ=2) # Type 2 ANOVA DataFrame
+        lm = ols(formula='percentual_k_unordered ~ algoritmo', data=data).fit()
+        anova = sm.stats.anova_lm(lm, typ=2) # Type 2 ANOVA DataFrame
 
         tit = ' ANOVA para Probabilidade = %s e Tamanho = %s' % (prob, tam)
         hr = '=' * 60 #len(tit)

### 2019-12-18 _fabiano/python/10-NOVO-2-Gerar TABELA ANOVA por Probabilidades de um mesmo Algoritmo.py

@@ -26,8 +26,8 @@ for alg in udata.ALGORTIMOS:
     # print(data.head())
     print(data['probabilidade_erro'].unique())
 
-    moore_lm = ols(formula='percentual_k_unordered ~ probabilidade_erro',data=data).fit()
-    anova = sm.stats.anova_lm(moore_lm, typ=2) # Type 2 ANOVA DataFrame
+    lm = ols(formula='percentual_k_unordered ~ probabilidade_erro', data=data).fit()
+    anova = sm.stats.anova_lm(lm, typ=2) # Type 2 ANOVA DataFrame
 
     tit = ' ANOVA para %s' % (alg.upper())
     hr = '=' * 70 #len(tit)

### 2019-12-18 _fabiano/python/11-NOVO-2-Gerar TABELA ANOVA 2 Fatores com repeticao-[Tam-Alg].py

@@ -1,0 +1,42 @@
+# import plotly.plotly as py
+# import plotly.graph_objs as go
+# from plotly.tools import FigureFactory as FF
+import os
+import sys
+import numpy as np
+import pandas as pd
+import scipy
+import scipy.stats as stats
+
+import statsmodels
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+import util_ler_dados as udata
+
+
+df_tudo = udata.obterDados2()
+
+arq_destino = '03-Anova-2/_ANOVA_TODAS_ANALISES_2_Fatores_com_Repeticao-[Tam-Alg].txt'
+if os.path.exists(arq_destino):
+    os.remove(arq_destino)
+arq_destino = open(arq_destino, 'w+')
+
+for prob in udata.PROBABILIDADES_2:
+    data = udata.obterDfPorProb2(prob=prob, df=df_tudo)
+    # print(data.head())
+
+    lm = ols(formula='percentual_k_unordered ~ algoritmo * size_of_array', data=data).fit()
+    anova = sm.stats.anova_lm(lm, typ=2) # Type 2 ANOVA DataFrame
+
+    tit = ' ANOVA para Probabilidade = %s ' % (prob)
+    hr = '=' * 60 #len(tit)
+    anov = anova.head(10)
+
+    s = '%s\n%s\n%s\n%s\n\n' %(hr,tit,hr,anov)
+    arq_destino.write(s)
+    print(s)
+
+
+#fecha arquivo
+arq_destino.close()
+

### 2019-12-18 _fabiano/python/12-NOVO-2-Gerar TABELA ANOVA 2 Fatores com repeticao-[Prob-Alg].py

@@ -1,0 +1,42 @@
+# import plotly.plotly as py
+# import plotly.graph_objs as go
+# from plotly.tools import FigureFactory as FF
+import os
+import sys
+import numpy as np
+import pandas as pd
+import scipy
+import scipy.stats as stats
+
+import statsmodels
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+import util_ler_dados as udata
+
+
+df_tudo = udata.obterDados2()
+
+arq_destino = '03-Anova-2/_ANOVA_TODAS_ANALISES_2_Fatores_com_Repeticao-[Prob-Alg].txt'
+if os.path.exists(arq_destino):
+    os.remove(arq_destino)
+arq_destino = open(arq_destino, 'w+')
+
+for tam in udata.TAMANHOS:
+    data = udata.obterDfPorTam2(tam=tam, df=df_tudo)
+    # print(data.head())
+
+    lm = ols(formula='percentual_k_unordered ~ algoritmo * probabilidade_erro', data=data).fit()
+    anova = sm.stats.anova_lm(lm, typ=2) # Type 2 ANOVA DataFrame
+
+    tit = ' ANOVA para Tamanho = %s ' % (tam)
+    hr = '=' * 60 #len(tit)
+    anov = anova.head(10)
+
+    s = '%s\n%s\n%s\n%s\n\n' %(hr,tit,hr,anov)
+    arq_destino.write(s)
+    print(s)
+
+
+#fecha arquivo
+arq_destino.close()
+

### 2019-12-18 _fabiano/python/13-NOVO-2-Gerar TABELA ANOVA 2 Fatores com repeticao-[Tam-Prob-Alg].py

@@ -1,0 +1,38 @@
+# import plotly.plotly as py
+# import plotly.graph_objs as go
+# from plotly.tools import FigureFactory as FF
+import os
+import sys
+import numpy as np
+import pandas as pd
+import scipy
+import scipy.stats as stats
+
+import statsmodels
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+import util_ler_dados as udata
+
+
+data = udata.obterDados2()
+
+arq_destino = '03-Anova-2/_ANOVA_TODAS_ANALISES_2_Fatores_com_Repeticao-[Tam-Prob-Alg].txt'
+if os.path.exists(arq_destino):
+    os.remove(arq_destino)
+arq_destino = open(arq_destino, 'w+')
+
+lm = ols(formula='percentual_k_unordered ~ algoritmo * probabilidade_erro * size_of_array', data=data).fit()
+anova = sm.stats.anova_lm(lm, typ=2)
+
+tit = ' ANOVA para ALgoritmo X Tamanho X Probabilidade'
+hr = '=' * 60 #len(tit)
+anov = anova.head(10)
+
+s = '%s\n%s\n%s\n%s\n\n' %(hr,tit,hr,anova.to_string())
+arq_destino.write(s)
+print(s)
+
+
+#fecha arquivo
+arq_destino.close()
+

### 2019-12-18 _fabiano/python/14-NOVO-2-Gerar TABELA ANOVA 2 Fatores com repeticao-[Prob-Tam].py

@@ -16,10 +16,10 @@ import util_ler_dados as udata
 
 df_tudo = udata.obterDados2()
 
-# arq_destino = '03-Anova-2/_ANOVA_TODAS_ANALISES_2_Fatores_com_Repeticao-[Prob-Alg].txt'
-# if os.path.exists(arq_destino):
-#     os.remove(arq_destino)
-# arq_destino = open(arq_destino, 'w+')
+arq_destino = '03-Anova-2/_ANOVA_TODAS_ANALISES_2_Fatores_com_Repeticao-[Prob-Tam].txt'
+if os.path.exists(arq_destino):
+    os.remove(arq_destino)
+arq_destino = open(arq_destino, 'w+')
 
 for alg in udata.ALGORTIMOS:
     data = udata.obterDfPorAlg2(alg=alg, df=df_tudo)
@@ -29,16 +29,16 @@ for alg in udata.ALGORTIMOS:
     anova = sm.stats.anova_lm(lm, typ=2) # Type 2 ANOVA DataFrame
 
     tit = ' ANOVA para Algoritmo = %s ' % (alg)
-    hr = '=' * 60 #len(tit)
+    hr = '=' * 110 #len(tit)
 
     anova['PR(>F) Rounded'] = anova['PR(>F)'].round(decimals=5)
 
 
     s = '%s\n%s\n%s\n%s\n\n' %(hr,tit,hr,anova.to_string())
-    # arq_destino.write(s)
+    arq_destino.write(s)
     print(s)
 
 
-# #fecha arquivo
-# arq_destino.close()
+#fecha arquivo
+arq_destino.close()
 

### 2019-12-18 _fabiano/python/util_ler_dados.py

@@ -90,6 +90,29 @@ def obterDfPorProbTam2(prob, tam, df=pd.DataFrame()):
     #
     return df_retorno
 
+def obterDfPorAlg2(alg, df=pd.DataFrame()):
+    if (df.empty):
+        df = obterDados2()
+    #
+    df_retorno = filtrarPorAlgoritmo(df, algoritmo=alg)
+    #
+    return df_retorno
+
+def obterDfPorTam2(tam, df=pd.DataFrame()):
+    if (df.empty):
+        df = obterDados2()
+    #
+    df_retorno = filtrarPorTamanhoArray(df, tamanho=tam)
+    #
+    return df_retorno
+
+def obterDfPorProb2(prob, df=pd.DataFrame()):
+    if (df.empty):
+        df = obterDados2()
+    #
+    df_retorno = filtrarPorProbabilidadeErro(df, prob=prob)
+    return df_retorno
+
 def obterDfPorProbAlg2(prob, alg, df=pd.DataFrame()):
     if (df.empty):
         df = obterDados2()

### 2019-12-19 paper/MaterialsAndMethods.tex
reestruturação do artigo.

@@
 Then, we provide our hypothesis, define the setup, and perform the testing.
-Finally, we collect and perform data and regression analysis.
+Finally, we collect and perform data analysis.
 
@@
 
-For this experimental study, we assume that the dependent and independent variables are as shown in Table \ref{table-variables} below:
+For this experimental study, we assume that the independent and dependent variables are as shown in Table \ref{table-independent-variables} and Table \ref{table-dependent-variables} below:
 
 \begin{table}[H]
-    \caption{Dependent and independent variables.}
+    \caption{Independent variables.}
     \begin{center}
-    \begin{tabular}{|c|c|}
+    \begin{tabular}{|l|l|}
     \hline
-    \multicolumn{2}{|c|}{\textbf{Variables}}\\
+    \textbf{Variable} & \textbf{Description} \\
     \hline
-    \textbf{\textit{Dependent}} & \textbf{\textit{Independent}} \\
+    Probability of failure & Probability of a fault to occur \\
     \hline
-    Largest subarray size & Probability of failure \\
-    Percentage of largest subarray size related to the original array & Array size \\
-    Unordered elements size & Sorting algorithm \\
-    Percentage of unordered elements size related to the original array & \\
+    Array size & Size of the array of integers to be sorted \\
+    \hline
+    Sorting algorithm & Algorithm used to sort the array \\
     \hline
     \end{tabular}
-    \label{table-variables}
+    \label{table-independent-variables}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \caption{Dependent variables.}
+    \begin{center}
+    \begin{tabular}{|l|l|}
+    \hline
+    \textbf{Variable} & \textbf{Description} \\
+    \hline
+    Largest subarray size & Size of the largest sorted subarray produced under the memory fault \\
+    \hline
+    Percentage of largest subarray size & Percentage of \textit{largest subarray size} related to \textit{array size} independent variable \\
+    \hline
+    Unordered elements quantity & Quantity of elements out of position after sorting algorithm execution.
+Adapted of the \\ & \textit{k-unordered sequence} measure of disorder defined in \cite{Ferraro-Petrillo2009} \\
+    \hline
+    Percentage of unordered elements quantity & Percentage of \textit{unordered elements quantity} related to \textit{array size} independent variable \\
+    \hline
+    \end{tabular}
+    \label{table-dependent-variables}
     \end{center}
@@
 
-We define a set of hypothesis to test and draw some conclusions. They are:
+The set of hypothesis defined to test and draw some conclusions about this experiment are listed below.
+The confidence degree defined for hypothesis testing was 95\% ($\alpha = 0.05$ and $\alpha - 1 = 0.95$).
 
-\setcounter{hyp}{-1}
-\begin{hyp}[Test hypothesis] \label{hyp:a}There is no difference in memory faults between tested algorithms.\end{hyp}
-\begin{hyp} \label{hyp:b}There are differences in memory faults between tested algorithms. \end{hyp}
-\begin{hyp} \label{hyp:c} An algorithm is better than others considering all dependent variables. \end{hyp}
+\begin{itemize}
+    \item \textbf{Hypothesis 1:} For a given probability of failure and array size, tested algorithms will produce a different percentage of unordered elements quantity.
+    \item \textbf{Hypothesis 2:} For a given probability of failure and array size, tested algorithms will produce a different percentage of the largest subarray size.
+    \item \textbf{Hypothesis 3:} For each algorithm, the array size and probability of failure have a significative impact on the percentage of unordered elements quantity.
+    \item \textbf{Hypothesis 4:} For each algorithm, the array size and probability of failure have a significative impact on the percentage of the largest subarray size.
+\end{itemize}
 
-\begin{hyp} \label{hyp:d} ... \end{hyp}
+% \setcounter{hyp}{-1}
+% \begin{hyp}[Test hypothesis] \label{hyp:a}There is no difference in memory faults between tested algorithms.\end{hyp}
+% \begin{hyp} \label{hyp:b}There are differences in memory faults between tested algorithms. \end{hyp}
+% \begin{hyp} \label{hyp:c} An algorithm is better than others considering all dependent variables. \end{hyp}
+
+% \begin{hyp} \label{hyp:d} ... \end{hyp}
 
@@
 \begin{itemize}
-    \item A file that contains a sequence of integers that are the input data;
+    \item A script that generates input files;
     \item Four files, one for each os those algorithms: quicksort, bubblesort, insertion sort, and mergesort, that are used to sorting the input data;
-    \item An output file with the sorted data.
 \end{itemize}

### 2019-12-20 paper/Background.tex

@@
 
-In this section, we'll provide some definitions of memory faults and used sorting algorithms.
+In this section we describe basic concepts about memory faults and sorting algorithms.
 
-\subsection{Memory Faults}
+\input{MemoryFaults}
 
-Despite the title of this subsection, when the entire digital system (or software) is considered, there are three terms for computing fault and they have different meanings: failure, fault and error.
-
-A failure denotes an element's inability to perform its functions because of error in the element itself or its environment.
-A fault is an anomalous physical condition.
-Causes include design errors, manufacturing problems, damage, fatigue, or other deterioration.
-Faults resulting from design errors and external factors are especially difficult to model and protect against because their occurrences and effects are hard to predict.
-An error is a manifestation of a fault in a system, in which the logical state of an element differs from its intended value.
-A fault in a system does not necessarily result in an error.
-An error occurs for a particular system state and input when an incorrect next state and/or output results \cite{Nelson1990}.
+\input{SortingAlgorithms}

### 2019-12-20 paper/SortingAlgorithms.tex

@@
-\section{Sorting Algorithms}
+\subsection{Sorting Algorithms}
 
@@
 
-\subsection{Quicksort}
+\subsubsection{Quicksort}
 
@@
 
-\subsection{Mergesort}
+\subsubsection{Mergesort}
 
@@
 
-\subsection{Insertionsort}
+\subsubsection{Insertionsort}
 
@@
 
-\subsection{Bubblesort}
+\subsubsection{Bubblesort}
 
@@
 It works by comparing each item in the list with the item next to it, and swapping them if required.
-The algorithm repeats this process until it makes a pass all the way through the list without swapping any items (in other words, all items are in the correct order) \cite{Mansotra2011}.
+The algorithm repeats this process until it makes a pass all the way through the list without swapping any items (in other words, all items are in the correct order) \cite{Mansotra2011}.\\
 

### 2019-12-20 _fabiano/python/02-NOVO-2-Medias_por_algoritmo_e_prob_erro.py
inserido docmento WORD com analise dos resultados

@@ -43,35 +43,42 @@ sizes = ['100','1000','10000']
 df_tudo = udata.obterDados2()
 
 #ordena os registros por algoritmo
-df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+df_tudo.sort_values(by=[udata.obterNomeColuna('size_of_array'),udata.obterNomeColuna('algoritmo')],
+                    inplace=True, ascending=[True,True])
 
 # gera os graficos
-rows = 5
+rows = 2 #5
 cols = 2
 
-larg_fig = 32
-alt_fig  = 41
-font_size = 15
+larg_fig = 38
+alt_fig  = 25
+font_size = 20
 
 sns_palette = 'Set2'
 color_map = sns.color_palette(sns_palette, n_colors=4)
 
 gerar_graficos = True
-gerar_csvs_com_dados_dos_graficos = True
+gerar_csvs_com_dados_dos_graficos = False
 
 df_dados_csv = pd.DataFrame()
 
 for prob in probs:
-    data = df_tudo[df_tudo.probabilidade_erro == float(prob)]
+    data = df_tudo[df_tudo[udata.obterNomeColuna('probabilidade_erro')] == float(prob)]
 
-    df_means = data.groupby(['size_of_array', 'algoritmo']).mean()
-    df_std = data.groupby(['size_of_array', 'algoritmo']).std()
-    df_min = data.groupby(['size_of_array', 'algoritmo']).min()
-    df_max = data.groupby(['size_of_array', 'algoritmo']).max()
+    group_by = [udata.obterNomeColuna('probabilidade_erro'), udata.obterNomeColuna('size_of_array'), udata.obterNomeColuna('algoritmo')]
+    df_means = data.groupby(group_by).mean().round(decimals=2)
+    df_median = data.groupby(group_by).median().round(decimals=2)
+    df_std = data.groupby(group_by).std().round(decimals=2)
+    df_min = data.groupby(group_by).min().round(decimals=2)
+    df_max = data.groupby(group_by).max().round(decimals=2)
 
     # colunas_join = ['largest_sorted_subarray','k_unordered_sequence','percentual_k_unordered','percentual_maior_array']
-    colunas_join = ['percentual_k_unordered','percentual_maior_array']
+    colunas_join = [udata.obterNomeColuna('percentual_k_unordered'),udata.obterNomeColuna('percentual_maior_array')]
[…]

### 2019-12-20 _fabiano/python/04-NOVO-2-Distribuicao_das_medidas_escolhidas.py

@@ -11,26 +11,21 @@ import seaborn as sns
 plt.style.use('seaborn-whitegrid')
 
 import util_graficos as graf
+import util_ler_dados as udata
 
-pasta_origem = '../data/data_grouped'
 
 alg = ['quick','bubble','merge','insertion']
-probs = [0.02,0.05]
-sizes = [100,1000,10000]
+probs = [0.01, 0.02, 0.05]
+sizes = [100, 1000, 10000]
 
-
-alg = ['quick','merge']
-alg = ['quick']
-probs = [0.01]
-sizes = [100]
 
 
 csv = 'data-csv-2/dados_extraidos-2.csv'
-df_tudo = pd.read_csv(delimiter = ';', filepath_or_buffer = csv)
-print(df_tudo)
+df_tudo = udata.obterDados2()
+# print(df_tudo)
 
 #ordena os registros por algoritmo
-df_tudo.sort_values(by=['size_of_array','algoritmo'], inplace=True, ascending=[True,True])
+df_tudo.sort_values(by=[udata.obterNomeColuna('size_of_array'),udata.obterNomeColuna('algoritmo')], inplace=True, ascending=[True,True])
 
 
 # gera os graficos
@@ -50,16 +45,16 @@ gerar_csvs_com_dados_dos_graficos = True
 df_dados_csv = pd.DataFrame()
 
 for prob in probs:
-    data = df_tudo[df_tudo.probabilidade_erro == float(prob)]
+    data = df_tudo[df_tudo[udata.obterNomeColuna('probabilidade_erro')] == float(prob)]
 
-    group_by = ['probabilidade_erro', 'algoritmo']
+    group_by = [udata.obterNomeColuna('probabilidade_erro'), udata.obterNomeColuna('algoritmo')]
     df_means = data.groupby(group_by).mean()
     df_std = data.groupby(group_by).std()
     df_min = data.groupby(group_by).min()
     df_max = data.groupby(group_by).max()
 
-    # colunas_join = ['largest_sorted_subarray','k_unordered_sequence','percentual_k_unordered','percentual_maior_array']
-    colunas_join = ['percentual_k_unordered','percentual_maior_array']
+    # colunas_join = ['largest_sorted_subarray','k_unordered_sequence',udata.obterNomeColuna('percentual_k_unordered'),udata.obterNomeColuna('percentual_maior_array')]
[…]

### 2019-12-20 _fabiano/python/07-NOVO-2-Gerar Histogramas Distribuicao.py

@@ -6,49 +6,49 @@ import matplotlib.font_manager as font_manager
 
 import numpy as np
 import pandas as pd
-
+import scipy.stats as stats
 import seaborn as sns
 import util_ler_dados as udata
 
 plt.style.use('seaborn-colorblind')
 
 
-def gerarHistograma(rows, cols, ind, plt, df, desc, prob, size, algo):
+def gerarHistograma(rows, cols, ind, plt, df, desc, bins):
     ax = plt.subplot(rows, cols, ind)
-    ax.set(xlabel=desc, ylabel='quantidade')
+    ax.set(ylabel='Quantity')#xlabel=desc,
     ax.axvline(float(df.median()), color='b')
     ax.axvline(float(df.mean()), color='r')
-    sns.distplot(df, ax=ax, bins=nbins, hist=True, kde=False)
+    sns.distplot(df, ax=ax, bins=bins, hist=True, kde=False)
     plt.title('%s' % (desc))  # , fontproperties=font_prop )
 
 
 #     plt.title('%s: %s (Prob: %s, Tam: %s)' % (algo, desc, prob, size))#, fontproperties=font_prop )
 
 
-def gerarKdeHistograma(rows, cols, ind, plt, df, desc, prob, size, algo):
+def gerarKdeHistograma(rows, cols, ind, plt, df, desc, bins):
     ax = plt.subplot(rows, cols, ind)
-    ax.set(xlabel=desc, ylabel='quantidade')
+    ax.set(ylabel='f(mean)') #xlabel=desc,
     ax.axvline(float(df.median()), color='b')
     ax.axvline(float(df.mean()), color='r')
-    sns.distplot(df, ax=ax, bins=nbins, hist=True, kde=True)
+    sns.distplot(df, ax=ax, bins=bins, hist=True, kde=True) #fit=stats.gamma
     plt.title('%s (KDE)' % (desc))  # , fontproperties=font_prop )
 
 
 #     plt.title('%s: %s (KDE) (Prob: %s, Tam: %s)' % (algo, desc, prob, size))#, fontproperties=font_prop )
 
 
-def gerarBoxplot(rows, cols, ind, plt, df, desc, prob, size, algo, palet='Set2'):
+def gerarBoxplot(rows, cols, ind, plt, df, desc, palet='Set2'):
     ax = plt.subplot(rows, cols, ind)
     ax.axhline(float(df.median()), color='b')
     ax.axhline(float(df.mean()), color='r')
[…]

### 2019-12-20 paper/MaterialsAndMethods.tex
continuação da escrita

@@
 
-To conduct the proposed study we get a set of files with the basic setup and instructions, that was composed by:
-\begin{itemize}
-    \item A script that generates input files;
-    \item Four files, one for each os those algorithms: quicksort, bubblesort, insertion sort, and mergesort, that are used to sorting the input data;
-\end{itemize}
+To conduct the proposed study, we define the values of the independent variables, as shown in Table \ref{table-independent-variables-values}:
 
-The input file looks like follow:
+\begin{table}[H]
+    \caption{Values of the independent variables.}
+    \begin{center}
+    \begin{tabular}{|c|c|}
+    \hline
+    \textbf{Variable} & \textbf{Values} \\
+    \hline
+    Probability of failure & 1\%, 2\% and 5\% \\
+    \hline
+    Array size & 100, 1000 and 10000 \\
+    \hline
+    Sorting algorithm & Bubblesort, Quicksort, Mergesort and Insertion sort \\
+    \hline
+    \end{tabular}
+    \label{table-independent-variables-values}
+    \end{center}
+\end{table}
+
+Based on these variables, we ran an existing script \textit{gen.py} to produce input files.
+We define that our sample was composed by 30 input files for a given combination of the probability of failure and array size.
+So, considering this, we ran 30 times for each combination of these independent variables, producing 30 inputs, totalizing 270 files.
+Figure \ref{fig-input-file-example} shows an example of produced input files:
+
+% \begin{itemize}
+%     \item A script that generates input files;
+%     \item Four files, one for each of those algorithms: quicksort, bubblesort, insertion sort, and mergesort, that are used to sorting the input data;
+% \end{itemize}
 
@@
 
-We run 1000 times each algorithm with each file listed in Table \ref{table-input-data} below.
+With this input data, we ran, for each one of these, all four algorithms considered in this study.
+The sorting algorithms used already existed.
+For example, using all 270 input files, we ran bubblesort, creating 270 output files, and so on for the other algorithms.
+At the end of executions, we get a total of 1080 output files.
+An output file look like shown in Figure \ref{fig-output-file-example}:
+
+% We run 1000 times each algorithm with each file listed in Table \ref{table-input-data} below.
 We chose this number of executions to reduce possible noise in the generated data.
@@
 
-For example, Input A showed in that table with its characteristics was executed 1000 times for each algorithm -  bubblesort, quicksort, mergesort, and insertion sort - totalizing 4000 executions.
+% For example, Input A showed in that table with its characteristics was executed 1000 times for each algorithm -  bubblesort, quicksort, mergesort, and insertion sort - totalizing 4000 executions.
 
-\begin{table}[H]
-    \caption{Generated input data.}
-    \begin{center}
-    \begin{tabular}{|c|c|c|c|c|}
-    \hline
-    \textbf{Input} & \textbf{Sequence Size} & \textbf{Probability of Failure} & \textbf{Executions} & \textbf{Algorithm} \\ 
-    \hline
-    \multirow{4}{*}{Input A} & \multirow{4}{*}{100} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input B} & \multirow{4}{*}{100} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input C} & \multirow{4}{*}{100} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input D} & \multirow{4}{*}{1000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input E} & \multirow{4}{*}{1000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input F} & \multirow{4}{*}{1000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input G} & \multirow{4}{*}{10000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input H} & \multirow{4}{*}{10000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \multirow{4}{*}{Input I} & \multirow{4}{*}{10000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-    & & & & Quicksort \\
-    & & & & Mergesort \\
-    & & & & Insertion Sort \\
-    \hline
-    \end{tabular}
-    \label{table-input-data}
-    \end{center}
-\end{table}
+% \begin{table}[H]
+%     \caption{Generated input data.}
+%     \begin{center}
+%     \begin{tabular}{|c|c|c|c|c|}
+%     \hline
+%     \textbf{Input} & \textbf{Sequence Size} & \textbf{Probability of Failure} & \textbf{Executions} & \textbf{Algorithm} \\ 
+%     \hline
+%     \multirow{4}{*}{Input A} & \multirow{4}{*}{100} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input B} & \multirow{4}{*}{100} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input C} & \multirow{4}{*}{100} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input D} & \multirow{4}{*}{1000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input E} & \multirow{4}{*}{1000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input F} & \multirow{4}{*}{1000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input G} & \multirow{4}{*}{10000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input H} & \multirow{4}{*}{10000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \multirow{4}{*}{Input I} & \multirow{4}{*}{10000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
+%     & & & & Quicksort \\
+%     & & & & Mergesort \\
+%     & & & & Insertion Sort \\
+%     \hline
+%     \end{tabular}
+%     \label{table-input-data}
+%     \end{center}
+% \end{table}
 
-Each execution generates an output file.
+% Each execution generates an output file.
 Then, we generate 4000 outputs for each combination of sequence size, and the probability of failure, totalizing 36000 files.
@@
 \end{itemize}
+
+After generating the dataset, we developed a Python script that reads the 1080 output files and produces a single CSV file (first lines showed in Figure \ref{fig-output-csv-file-example} below), containing the following columns:
+\begin{itemize}
+    \item \textit{algorithm}: the algorithm used to sort the array;
+    \item \textit{probability\_of\_failure}: the probability of failure used when sorting;
+    \item \textit{size\_of\_array}: the size of the array to be sorted;
+    \item \textit{largest\_sorted\_subarray}: the largest sorted subarray after sorting;
+    \item \textit{k\_unordered\_sequence}: number of unordered sequence after sorting.
+    \item \textit{percentage\_k\_unordered}: percentage of unordered sequence after sorting related to original array;
+    \item \textit{percentage\_largest\_sorted\_subarray}: percentage of largest sorted subarray after sorting related to original array.
+\end{itemize}
+
+\begin{verbbox}[\mbox{}]
+algorithm;probability_of_failure;size_of_array;largest_sorted_subarray;
+k_unordered_sequence;percentage_k_unordered;
+percentage_largest_sorted_subarray
+quick;0.01;100;35;4;4.00;35.00
+quick;0.01;100;36;8;8.00;36.00
+quick;0.01;100;31;5;5.00;31.00
+quick;0.01;100;20;6;6.00;20.00
+quick;0.01;100;31;5;5.00;31.00
+\end{verbbox}
+
+\begin{figure}[H]
+    \centering
+    \fbox{
+    \theverbbox
+    }
+    \caption{Example of output CSV file.}
+    \label{fig-output-csv-file-example}
+\end{figure}
 

### 2019-12-21 paper/MaterialsAndMethods.tex
finalização do experimental setup

@@
 
+We use Python libraries to make data analysis and plot graphs. These libraries were:
+\begin{itemize}
+    \item \textit{Pandas\footnote{https://pandas.pydata.org}}: open source library providing data structures and data analysis tools;
+    \item \textit{NumPy\footnote{https://numpy.org}}: library for scientific computing with Python;
+    \item \textit{SciPy\footnote{https://www.scipy.org}}: ecosystem of open-source software for mathematics, science, and engineering;
+    \item \textit{StatsModels\footnote{https://www.statsmodels.org}}: module that provides classes and functions for the estimation of many different statistical models, as well as for conducting statistical tests, and statistical data exploration;
+    \item \textit{Matplotlib\footnote{https://matplotlib.org}}: plotting library;
+    \item \textit{Seaborn\footnote{https://seaborn.pydata.org}}: data visualization library based on matplotlib.
+\end{itemize}
+
 \subsection{Development}

### 2019-12-21 paper/DataAnalysis.tex
continuacao da escrita

\section{Data Analysis}

In this section, we present our results after the execution of sorting algorithms over the input files. We analyzed only the dependent variables \textit{percentage of the largest subarray size ((\%LSS)} and \textit{percentage of unordered elements quantity (\%UEQ)}. These variables, because they are a percentage value, already were normalized (i.e., the same order of magnitude) related to dependent variable array size.

\subsection{Exploratory Data Analysis (EDA)}

Firstly, we performed an analysis of the distribution of the dependent variables \%LSS and \%UEQ. To help in this task, we produced histograms, boxplot graphs, tables containing data about mean, median, standard deviation, and the minimum and maximum values.

The following Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000} illustrates examples of histograms and boxplot graphs for each combination of \textit{Algorithm X Probability of Failure X Array Size}. In each of those figures, the graphs were exhibited over the dependent variables \%LSS and \%UEQ.  In the histogram, the red vertical line means the mean, and the blue vertical line means the median. On the other hand, in the boxplot, the red horizontal line means the mean, and the blue horizontal line means the median.

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_01_100_Bubble.png}}
    \caption{Histograms and Boxplot for Bubblesort, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
    \label{fig-histogram-boxplot-bubble-001100}
\end{figure}

Based on Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000}, the following tables illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.

\begin{table}[H]
    \caption{Table Type Styles}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \textbf{Prob. of Failure} & \textbf{Array Size} & \multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
    \cline{2-4} 
     & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
    \hline
    copy & adsad & asdasd & asdasd \\
    \hline
    \end{tabular}
    \label{tab-distribution-depentent-variable-ueq}
    \end{center}
\end{table}

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_01_100_Insertion.png}}
    \caption{Histograms and Boxplot for Insertion sort, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
    \label{fig-histogram-boxplot-insertion-001100}
\end{figure}

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_05_10000_Merge.png}}
    \caption{Histograms and Boxplot for Mergesort, with \textit{probability of failure} of 0.05 and \textit{array size} of 10000.}
    \label{fig-histogram-boxplot-merge-00510000}
\end{figure}

\begin{figure}[H]
    \centering
    \frame{\includegraphics[scale=0.105]{figures/0_05_10000_Quick.png}}
    \caption{Histograms and Boxplot for Quicksort, with \textit{probability of failure} of 0.05 and \textit{array size} of 10000.}
    \label{fig-histogram-boxplot-quick-00510000}
\end{figure}

We produced graphs with the same data about dependent variables showed in tables before. Figure X shows an example of these graphs.

### 2019-12-21 paper/ExperimentalSetup.tex
continuacao da escrita

--- 2019-12-21 paper/MaterialsAndMethods.tex
@@
-\section{Materials and Methods}
+\section{Experimental Setup}
 
@@
 
-\subsection{Experimental Setup}
+\subsection{Dataset}
 
@@
 
-\subsection{Development}
+% \subsection{Data Analysis}
 
-We develop Python scripts to generate our dataset.
-First, we generate all input files through a given script called \textit{gen.py}.
-This script considers sequence size and the probability of failure to create a sequence of integers.
-Were produced nine input files like Figure \ref{fig-input-file-example}, combining the sequence size and probability of failure listed in Table \ref{table-input-data}.
+% In this section, we describe our data and the statistic tests used to test the hypothesis showed before.
 
-After that, we developed a script called \textit{main\_execution.py} that is responsible for creating output files based on the input files exposed before.
-At this time, for every input showed in Table \ref{table-input-data} we ran 1000 times to minimize any deviation on the quality of sorting indicator (line \textit{[4]} on Figure \ref{fig-output-file-example}).
+% \subsubsection{Exploratory Data Analysis (EDA)}
 
-As said before, after the execution of this algorithm, 4000 outputs for each combination of sequence size, and the probability of failure, totalizing 36000 files.
-
-\textcolor{red}{To be continued...}
-
-\subsection{Data Analysis}
-
-In this section, we describe our data and the statistic tests used to test the hypothesis showed before.
-
-\subsubsection{Exploratory Data Analysis (EDA)}
-
-Based on the output files generated before, our starting point was to test if the dataset had a normal distribution.
+% Based on the output files generated before, our starting point was to test if the dataset had a normal distribution.
 To achieve this, we use Shapiro-Wilk normality test.
@@
 
-\begin{figure}[H]
-    \centering
-     \begin{subfigure}{.5\textwidth}
-     \centering
-     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Bubble_distribution_graph}}
-     \textsf{\caption[Distribution Graph for bubblesort.]{Distribution Graph for bubblesort.\label{fig-dist-bubble-001-100}}}
-     \end{subfigure}%
-     \begin{subfigure}{.5\textwidth}
-     \centering
-     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Insertion_distribution_graph.png}}
-     \textsf{\caption[Distribution Graph for insertion sort.]{Distribution Graph for insertion sort.\label{fig-dist-insertion-001-100}}}
-     \end{subfigure}
-     \begin{subfigure}{.5\textwidth}
-     \centering
-     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Merge_distribution_graph.png}}
-     \textsf{\caption[Distribution Graph for mergesort.]{Distribution Graph for mergesort.\label{fig-dist-merge-001-100}}}
-     \end{subfigure}%
-     \begin{subfigure}{.5\textwidth}
-     \centering
-     \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Quick_distribution_graph.png}}
-     \textsf{\caption[Distribution Graph for quicksort.]{Distribution Graph for quicksort.\label{fig-dist-quick-001-100}}}
-     \end{subfigure}
-     \caption{Distribution graph for a probability failure of 1\% and a sequence size of 10000.}
-    \label{fig-distribution-graph}
-\end{figure}
+% \begin{figure}[H]
+%     \centering
+%      \begin{subfigure}{.5\textwidth}
+%      \centering
+%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Bubble_distribution_graph}}
+%      \textsf{\caption[Distribution Graph for bubblesort.]{Distribution Graph for bubblesort.\label{fig-dist-bubble-001-100}}}
+%      \end{subfigure}%
+%      \begin{subfigure}{.5\textwidth}
+%      \centering
+%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Insertion_distribution_graph.png}}
+%      \textsf{\caption[Distribution Graph for insertion sort.]{Distribution Graph for insertion sort.\label{fig-dist-insertion-001-100}}}
+%      \end{subfigure}
+%      \begin{subfigure}{.5\textwidth}
+%      \centering
+%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Merge_distribution_graph.png}}
+%      \textsf{\caption[Distribution Graph for mergesort.]{Distribution Graph for mergesort.\label{fig-dist-merge-001-100}}}
+%      \end{subfigure}%
+%      \begin{subfigure}{.5\textwidth}
+%      \centering
+%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Quick_distribution_graph.png}}
+%      \textsf{\caption[Distribution Graph for quicksort.]{Distribution Graph for quicksort.\label{fig-dist-quick-001-100}}}
+%      \end{subfigure}
+%      \caption{Distribution graph for a probability failure of 1\% and a sequence size of 10000.}
+%     \label{fig-distribution-graph}
+% \end{figure}
 
-Q-Q plot shows that how much more blue points close to the red line, most normal is the distribution.
+% Q-Q plot shows that how much more blue points close to the red line, most normal is the distribution.
 Figure \ref{fig-qqplot} below presents this graph for a probability failure of 1\% and a sequence size of 10000 for considered sorting algorithms.
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.37]{figures/anova_prob_0_01_tam_10000_DESORDENADOS_PERCENTUAL.png}
-    \textsf{\caption[Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.]{Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.\label{fig-qqplot}}}
- \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.37]{figures/anova_prob_0_01_tam_10000_DESORDENADOS_PERCENTUAL.png}
+%     \textsf{\caption[Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.]{Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.\label{fig-qqplot}}}
+%  \end{figure}
 

### 2019-12-21 paper/article.tex
adicao de imagens e continuacao da escrita
reestruturação do artigo.
continuacao da escrita

@@
 \usepackage{thmtools}
+\usepackage{float}
+\usepackage{subcaption} % usado para figuras lado a lado
 
@@
 
-\input{MemoryFaults}
+\input{Background}
 
-\input{SortingAlgorithms}
+\input{ExperimentalSetup}
 
-\input{MaterialsAndMethods}
+\input{DataAnalysis}
 
@@
 \input{Conclusion}
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
 
@@
 
-% \begin{figure}[htbp]
-% \centerline{\includegraphics{fig1.png}}
-% \caption{Example of a figure caption.}
-% \label{fig}
-% \end{figure}
-
 Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 

### 2019-12-21 paper/DataAnalysis.tex
continuação da escrita.

@@
 
-Based on Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000}, the following tables illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.
+Based on Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000}, the following Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss} illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.
 
@@
     \begin{center}
-    \begin{tabular}{|c|c|c|c|c|}
+    \begin{tabular}{|c|c|c|c|c|c|c|c|}
     \hline
-    \textbf{Prob. of Failure} & \textbf{Array Size} & \multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-    \cline{2-4} 
-     & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of unordered elements quantity (\%UEQ)}} \\
+    \cline{4-8} 
+    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
     \hline
-    copy & adsad & asdasd & asdasd \\
+    0.01 & 100 & bubble & 3.07 & 3.0 & 1.64 & 0.0 & 6.0 \\
+    \hline
+    0.01 & 100 & insertion & 10.87 & 11.0 & 1.59 & 8.0 & 14.0 \\
+    \hline
+    0.05 & 10000 & merge & 28.32 & 28.34 & 0.31 & 27.69 & 28.86 \\
+    \hline
+    0.05 & 10000 & quick & 19.56 & 19.58 & 0.26 & 18.95 & 20.07 \\
     \hline
@@
 \end{figure}
+
+\begin{table}[H]
+    \caption{Table Type Styles}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|c|c|c|c|}
+    \hline
+    \textbf{Prob. of Failure} & \textbf{Array Size} & \textbf{Algorithm} & \multicolumn{5}{|c|}{\textbf{Percentage of largest subarray size (\%LSS)}} \\
+    \cline{4-8} 
+    & & & \textbf{\textit{Mean}}& \textbf{\textit{Median}} & \textbf{\textit{Std. Deviation}} & \textbf{\textit{Minimum}} & \textbf{\textit{Maximum}} \\
+    \hline
+    0.01 & 100 & bubble & 67.4 & 71.0 & 15.84 & 38.0 & 100.0 \\
+    \hline
+    0.01 & 100 & insertion & 19.77 & 20.0 & 3.11 & 14.0 & 27.0 \\
+    \hline
+    0.05 & 10000 & merge & 0.19 & 0.2 & 0.03 & 0.15 & 28.86 \\
+    \hline
+    0.05 & 10000 & quick & 0.3 & 0.3 & 0.03 & 0.23 & 0.34 \\
+    \hline
+    \end{tabular}
+    \label{tab-distribution-depentent-variable-lss}
+    \end{center}
+\end{table}
 
@@
 
-We produced graphs with the same data about dependent variables showed in tables before. Figure X shows an example of these graphs.
+We produced graphs with the same data showed in Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss}.
+Figure \ref{fig-distribution-all-algorithms-001-all-sizes} shows an example of these graphs.
+On it, we illustrate on the top-left graph that, considering the mean, bubblesort produces fewer unordered elements related to the total than other algorithms.
+
+\begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=0.20]{figures/Estatisticas_por_Algoritmo_Prob_001.png}}
+    \caption{Distribution data with \textit{probability of failure} of 0.01, all algorithms and \textit{array sizes}.}
+    \label{fig-distribution-all-algorithms-001-all-sizes}
+\end{figure}
+
+\subsection{Dependente Variables Normality}
+
+An essential step to continue the analysis is to verify if dependent variables have a normal distribution.
+In this work, we produced the Q-Q plot to analyze the normality visually.
+We also ran the Shapiro-Wilk \cite{shapiro1965analysis} test to confirm if they follow a normal distribution or not.
+
+After the Shapiro-Wilk test, we determine that only the dependent variable \%UEQ (\textit{percentage of unordered elements quantity}) has a normal distribution related to mean for all algorithms.
+This situation occurs considering all possible combinations between independent variables: \textit{sorting algorithm}, \textit{probability of failure} and \textit{array size}.
+
+Based on these results, we choose to test just the hypothesis associated with the dependent variable \%UEQ.
+We make use of the ANOVA method to test the hypothesis, and this method is premised the normal distribution of variables values.
+
+Tables \ref{table-shapiro-test-lss} and \ref{table-shapiro-test-ueq} shows examples of results we get running Shapiro-Wilk test.
+The independent variables assume these values: \textit{probability of failure} of 0.01 and \textit{array size} of 100.
+The bold \textit{p-values} confirms that the data is normally distributed.
+
+\begin{table}[H]
+    \parbox{.45\linewidth}{
+        \caption{Shapiro-Wilk test for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.}
+        \begin{center}
+        \begin{tabular}{|c|c|c|}
+        \hline
+        \textbf{Algorithm} & \textbf{W} & \textbf{p-value} \\
+        \hline
+        Bubblesort & 0.854840 & 0.0007 \\
+        \hline
+        Insertion Sort & 0.961790 & \textbf{0.3439} \\
+        \hline
+        Mergesort & 0.937173 & \textbf{0.0763} \\
+        \hline
+        Quicksort & 0.869708 & 0.0016 \\
+        \hline
+        \end{tabular}
+        \label{table-shapiro-test-lss}
+        \end{center}
+    }
+    \hfill
+    \parbox{.45\linewidth}{
+        \caption{Shapiro-Wilk test for \%UEQ with \textit{probability of failure} of 1\% and \textit{array size} of 100.}
+        \begin{center}
+        \begin{tabular}{|c|c|c|}
+        \hline
+        \textbf{Algorithm} & \textbf{W} & \textbf{p-value} \\
+        \hline
+        Bubblesort & 0.934980 & \textbf{0.0666} \\
+        \hline
+        Insertion Sort & 0.949881 & \textbf{0.1678} \\
+        \hline
+        Mergesort & 0.936667 & \textbf{0.0739} \\
+        \hline
+        Quicksort & 0.936049 & \textbf{0.0712} \\
+        \hline
+        \end{tabular}
+        \label{table-shapiro-test-ueq}
+        \end{center}
+    }
+\end{table}
+
+Q-Q plot shows that how much more blue points close to the red line, most normal is the distribution.
+Figure \ref{fig-qqplot-lss-001-100} below presents this graph for the dependent variable \textit{percentage of the largest subarray size} considering a \textit{probability of failure} of 1\% and a \textit{array size} of 100 for all sorting algorithms.
+
+\begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_01_tam_100_Largest_subarray_size.png}}
+    \textsf{\caption[Q-Q plot for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.]{Q-Q plot for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.\label{fig-qqplot-lss-001-100}}}
+ \end{figure}
+
+ Figure \ref{fig-qqplot-ueq-001-100} shows the same graph for the dependent variable \textit{percentage of unordered elements quantity} considering same values for independent variables.
+
+\begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_01_tam_100_Perc_unordered_elements_quantity.png}}
+    \textsf{\caption[Q-Q plot for \%UEQ with \textit{probability of failure} of 1\% and \textit{array size} of 100.]{Q-Q plot for \%UEQ with \textit{probability of failure} of 1\% and \textit{array size} of 100.\label{fig-qqplot-ueq-001-100}}}
+\end{figure}

### 2019-12-21 paper/article.tex
continuação da escrita.

@@
 
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
+% \subsection{Figures and Tables}
+% \paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
+% bottom of columns. Avoid placing them in the middle of columns. Large 
+% figures and tables may span across both columns. Figure captions should be 
+% below the figures; table heads should appear above the tables. Insert 
+% figures and tables after they are cited in the text. Use the abbreviation 
+% ``Fig.~\ref{fig}'', even at the beginning of a sentence.
 
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
+% \begin{table}[htbp]
+% \caption{Table Type Styles}
+% \begin{center}
+% \begin{tabular}{|c|c|c|c|}
+% \hline
+% \textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+% \cline{2-4} 
+% \textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+% \hline
+% copy& More table copy$^{\mathrm{a}}$& &  \\
+% \hline
+% \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+% \end{tabular}
+% \label{tab1}
+% \end{center}
+% \end{table}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+% Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
+% rather than symbols or abbreviations when writing Figure axis labels to 
+% avoid confusing the reader. As an example, write the quantity 
+% ``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
+% units in the label, present them within parentheses. Do not label axes only 
+% with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
+% \{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
+% quantities and units. For example, write ``Temperature (K)'', not 
+% ``Temperature/K''.
 
-\section*{Acknowledgment}
+% \section*{Acknowledgment}
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+% The preferred spelling of the word ``acknowledgment'' in America is without 
+% an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+% G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+% acknowledgments in the unnumbered footnote on the first page.
 

### 2019-12-22 paper/Conclusion.tex
finalização da escrita do artigo

\section{Conclusion}

This work proposes a study and discussion of how sorting algorithms, particularly Quicksort, Mergesort, Insertion Sort, and Bubblesort, are affected by memory faults. To achieve this, we define the experimental setup, showing the dependent and independent variables, then the used dataset with its characteristics. Next, we performed data analysis after the execution of sorting algorithms over the dataset. As explained in this work, we analyzed only the dependent variables \textit{percentage of the largest subarray size ((\%LSS)} and \textit{percentage of unordered elements quantity (\%UEQ)}. These variables, because they are a percentage value, already were normalized (i.e., the same order of magnitude) related to dependent variable \textit{array size}.

We ran a normality test and, after that, we determined that only the dependent variable \%UEQ (\textit{percentage of unordered elements quantity}) has a normal distribution related to mean for all algorithms, so we choosed to test just the hypothesis associated with the dependent variable \%UEQ.

After data analysis and discussion, we can conclude that, in this experiment, the worse algorithm related to \%UEQ variable was Insertion sort. This algorithm had the highest mean values in almost all combinations of study. These values were much higher than other algorithms when tested with \textit{probability of failure} of 1\% (0.01). Finally, our tests shows that, in general, Quicksort algorithm was better than Mergesort.

We can, then, with our results, elaborate a ranking of the performance of algorithms when considering memory faults:
\begin{enumerate}
    \item Bubblesort
    \item Quicksort
    \item Mergesort
    \item Insertion sort
\end{enumerate}

### 2019-12-22 paper/DataAnalysis.tex
finalização da escrita do artigo

@@
 We analyzed only the dependent variables \textit{percentage of the largest subarray size ((\%LSS)} and \textit{percentage of unordered elements quantity (\%UEQ)}.
-These variables, because they are a percentage value, already were normalized (i.e., the same order of magnitude) related to dependent variable array size.
+These variables, because they are a percentage value, already were normalized (i.e., the same order of magnitude) related to dependent variable \textit{array size}.
 
@@
 
-\subsection{Dependente Variables Normality}
+\subsection{Dependent Variables Normality}
 
@@
 
-Tables \ref{table-shapiro-test-lss} and \ref{table-shapiro-test-ueq} shows examples of results we get running Shapiro-Wilk test.
+Tables \ref{table-shapiro-test-lss-001-100} and \ref{table-shapiro-test-ueq-001-100} shows examples of results we got running Shapiro-Wilk test.
 The independent variables assume these values: \textit{probability of failure} of 0.01 and \textit{array size} of 100.
@@
         \end{tabular}
-        \label{table-shapiro-test-lss}
+        \label{table-shapiro-test-lss-001-100}
         \end{center}
@@
         \end{tabular}
-        \label{table-shapiro-test-ueq}
+        \label{table-shapiro-test-ueq-001-100}
         \end{center}
@@
     \centering
-    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_01_tam_100_Largest_subarray_size.png}}
+    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_01_tam_100_Perc_largest_subarray_size.png}}
     \textsf{\caption[Q-Q plot for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.]{Q-Q plot for \%LSS with \textit{probability of failure} of 1\% and \textit{array size} of 100.\label{fig-qqplot-lss-001-100}}}
@@
 \end{figure}
+
+Tables \ref{table-shapiro-test-lss-005-1000} and \ref{table-shapiro-test-ueq-005-1000} shows another examples of results we got running Shapiro-Wilk test.
+The independent variables assume these values: \textit{probability of failure} of 0.05 and \textit{array size} of 1000.
+The bold \textit{p-values} confirms that the data is normally distributed.
+
+\begin{table}[H]
+    \parbox{.45\linewidth}{
+        \caption{Shapiro-Wilk test for \%LSS with \textit{probability of failure} of 5\% and \textit{array size} of 1000.}
+        \begin{center}
+        \begin{tabular}{|c|c|c|}
+        \hline
+        \textbf{Algorithm} & \textbf{W} & \textbf{p-value} \\
+        \hline
+        Bubblesort & 0.891642 & 0.00052 \\
+        \hline
+        Insertion Sort & 0.921918 & 0.3000 \\
+        \hline
+        Mergesort & 0.878308 & 0.0025 \\
+        \hline
+        Quicksort & 0.917583 & 0.0232 \\
+        \hline
+        \end{tabular}
+        \label{table-shapiro-test-lss-005-1000}
+        \end{center}
+    }
+    \hfill
+    \parbox{.45\linewidth}{
+        \caption{Shapiro-Wilk test for \%UEQ with \textit{probability of failure} of 5\% and \textit{array size} of 1000.}
+        \begin{center}
+        \begin{tabular}{|c|c|c|}
+        \hline
+        \textbf{Algorithm} & \textbf{W} & \textbf{p-value} \\
+        \hline
+        Bubblesort & 0.936459 & \textbf{0.0730} \\
+        \hline
+        Insertion Sort & 0.931681 & \textbf{0.0544} \\
+        \hline
+        Mergesort & 0.961920 & \textbf{0.3465} \\
+        \hline
+        Quicksort & 0.963954 & \textbf{0.3892} \\
+        \hline
+        \end{tabular}
+        \label{table-shapiro-test-ueq-005-1000}
+        \end{center}
+    }
+\end{table}
+
+Other examples of distribution normality can be seen in Q-Q plot in Figures \ref{fig-qqplot-lss-005-1000} and Y below.
+The considered dependent variable is \textit{percentage of the largest subarray size} with a \textit{probability of failure} value of 5\% and \textit{array size} value of 10000 for all sorting algorithms.
+
+\begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_05_tam_1000_Perc_largest_subarray_size.png}}
+    \textsf{\caption[Q-Q plot for \%LSS with \textit{probability of failure} of 5\% and \textit{array size} of 1000.]{Q-Q plot for \%LSS with \textit{probability of failure} of 5\% and \textit{array size} of 1000.\label{fig-qqplot-lss-005-1000}}}
+ \end{figure}
+
+ \begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=0.30]{figures/anova_prob_0_05_tam_1000_Perc_unordered_elements_quantity.png}}
+    \textsf{\caption[Q-Q plot for \%UEQ with \textit{probability of failure} of 5\% and \textit{array size} of 1000.]{Q-Q plot for \%UEQ with \textit{probability of failure} of 5\% and \textit{array size} of 1000.\label{fig-qqplot-ueq-005-1000}}}
+ \end{figure}
+
+ \subsection{Hypothesis Testing}
+
+ For hypothesis testing, we define a confidence degree of 95\%.
+As mentioned before, we only tested the hypothesis related to the dependent variable \%UEQ \textit{percentage of unordered elements quantity}.
+The hypothesis was:
+ \begin{itemize}
+     \item \textbf{Hypothesis 1}: For a given probability of failure and array size, tested algorithms will produce a different percentage of unordered elements quantity;
+     \item \textbf{Hypothesis 3}: For each algorithm, the array size and probability of failure have a significative impact on the percentage of unordered elements quantity.
+ \end{itemize}
+
+ Because our dataset has 3 independent variables, we perform ANOVA method to simplify the hypothesis testing. This method allows comparing various groups of variables at the same time.
+
+ \subsubsection{Testing Hypothesis 1}
+
+We formulated the following hypothesis for the combination of independent variables \textit{probability of failure} and \textit{array size}:
+
+\setcounter{hyp}{-1}
+\begin{hyp} \label{hyp:a} There is no significant difference between algorithms related to variable \%UEQ.\end{hyp}
+\begin{hyp} \label{hyp:b} There is significant difference between algorithms related to variable \%UEQ.\end{hyp}
+
+After we run the testing method, we got the following results (Table \ref{tab-hypothesis1-testing}):
+
+\begin{table}[H]
+    \caption{Hypothesis 1 ANOVA results.}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 1\% and Array Size = 100}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 1174.466667 & 3.0 & 171.368721 & \textbf{1.845762e-42} \\
+    \hline
+    residual & 265.000000 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 1\% and Array Size = 1000}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 1635.180250 & 3.0 & 1817.615579 & \textbf{2.610034e-97} \\
+    \hline
+    residual & 34.785667 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 1\% and Array Size = 10000}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 1948.204989 & 3.0 & 15831.708335 & \textbf{2.332995e-151} \\
+    \hline
+    residual & 4.758210 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 2\% and Array Size = 100}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 1106.5 & 3.0 & 88.617785 & \textbf{7.054900e-30} \\
+    \hline
+    residual & 482.8 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 2\% and Array Size = 1000}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 2286.83025 & 3.0 & 1990.144336 & \textbf{1.507899e-99} \\
+    \hline
+    residual & 44.43100 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 2\% and Array Size = 10000}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 3081.306943 & 3.0 & 18442.105239 & \textbf{3.406264e-155} \\
+    \hline
+    residual & 6.460427 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 5\% and Array Size = 100}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 2274.291667 & 3.0 & 225.58173 & \textbf{3.104916e-48} \\
+    \hline
+    residual & 389.833333 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 5\% and Array Size = 1000}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 3704.037583 & 3.0 & 1202.21591 & \textbf{3.625400e-87} \\
+    \hline
+    residual & 119.132333 & 116.0 & & \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Probablity of Failure = 5\% and Array Size = 10000}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    algorithm & 4948.821397 & 3.0 & 19487.120298 & \textbf{1.402080e-156} \\
+    \hline
+    residual & 9.819533 & 116.0 & & \\
+    \hline
+    \end{tabular}
+    \label{tab-hypothesis1-testing}
+    \end{center}
+\end{table}
+
+Based on these results, we reject the null hypothesis ($H_{0}$) for all testing combinations.
+Therefore, we can affirm with 95\% of confidence that there is a significant difference between algorithms related do variable \%UEQ.
+
+\subsubsection{Testing Hypothesis 3}
+
+We formulated the following hypothesis for all algorithms considered in this work:
+
+\setcounter{hyp}{-1}
+\begin{hyp} \label{hyp:a} The values of variables \textit{probability of failure} and \textit{array size} don't have a significant impact on values of \%UEQ variable.\end{hyp}
+\begin{hyp} \label{hyp:b} The values of variables \textit{probability of failure} and \textit{array size} have a significant impact on values of \%UEQ variable.\end{hyp}
+
+After we run the testing method, we got the following results (Table \ref{tab-hypothesis3-testing}):
+
+\begin{table}[H]
+    \caption{Hypothesis 3 ANOVA results}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Bubblesort}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    size\_of\_array & 0.019548 & 1.0 & 0.01350 & \textbf{0.90759} \\
+    \hline
+    probability\_of\_failure & 3590.644437 & 1.0 & 2479.71637 & \textbf{7.570027e-137} \\
+    \hline
+    residual & 385.169623 & 266.0 & &  \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Mergesort}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    size\_of\_array & 1784.873256 & 1.0 & 383.585800 & \textbf{1.702008e-53} \\
+    \hline
+    probability\_of\_failure & 13009.963175 & 1.0 & 2795.961630 & \textbf{3.801570e-143} \\
+    \hline
+    residual & 1237.731651 & 266.0 & &  \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Quicksort}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    size\_of\_array & 121.551362 & 1.0 & 32.964196 & \textbf{2.556033e-08} \\
+    \hline
+    probability\_of\_failure & 5626.955128 & 1.0 & 1526.005558 & \textbf{3.457996e-112} \\
+    \hline
+    residual & 980.841817 & 266.0 & &  \\
+    \hline
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Insertion sort}} \\
+    \cline{2-5}
+    &\textbf{\textit{sum\_sq}} & \textbf{\textit{df}} & \textbf{\textit{F}} & \textbf{\textit{PR(>F)}} \\
+    \hline
+    size\_of\_array & 309.843991 & 1.0 & 75.905868 & \textbf{3.236586e-16} \\
+    \hline
+    probability\_of\_failure & 6806.075083 & 1.0 & 1667.358570 & \textbf{1.414758e-116} \\
+    \hline
+    residual & 1085.798822 & 116.0 & & \\
+    \hline
+    \end{tabular}
+    \label{tab-hypothesis3-testing}
+    \end{center}
+\end{table}
+
+Based on these results, we reject the null hypothesis ($H_{0}$) for algorithms Mergesort, Quicksort, and Insertion sort.
+Therefore, we can affirm with 95\% of confidence that the values of variables \textit{probability of failure} and \textit{array size} have a significant impact on values of \%UEQ variable.
+
+For Bubblesort algorithm, however, there is no confidence to reject the null hypothesis ($H_{0}$).
+Analyzing the result, we can affirm with 95\% of confidence that the value of \textit{probability of failure} variable had a significant impact on the value of the dependent variable \%UEQ.
+But we can't affirm the same related to independent variable \textit{array size}.
+These results demonstrate that, for Bubblesort algorithm, the array sizes used in this experiment were not decisive to define values concerning the percentage of unordered elements quantity.
+
+\subsection{Performance analysis related to \textit{percentage of unordered elements quantity} variable}
+
+In this section, we present an analysis of overall performance related to dependent variable \textit{percentage of unordered elements quantity}.
+To help this analysis, we show below 3 bar graphs, each of these for a different value of \textit{probability of failure} independent variable.
+These graphs shows informations about values of \%UEQ variable grouped by \textit{array size} and \textit{sorting algorithm} variables.
+Figures \ref{fig-barplot-pof-001}, \ref{fig-barplot-pof-002}, and \ref{fig-barplot-pof-005} below exhibit these graphs.
+
+The bars in each graph represents the sample mean value for variable \%UEQ inside each group.
+Above each bar, there is a vertical line that indicates the lower and upper limits of a confidence interval for a significance level of 5\% ($\alpha = 0.05$).
+
+\begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=1.15]{figures/Barplot_Estatisticas_por_Algoritmo_Prob_0_01.png}}
+    \textsf{\caption[Data for \textit{probability of failure} of 1\%.]{Data for \textit{probability of failure} of 1\%.\label{fig-barplot-pof-001}}}
+ \end{figure}
+
+ \begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=1.15]{figures/Barplot_Estatisticas_por_Algoritmo_Prob_0_02.png}}
+    \textsf{\caption[Data for \textit{probability of failure} of 2\%.]{Data for \textit{probability of failure} of 2\%.\label{fig-barplot-pof-002}}}
+ \end{figure}
+
+ \begin{figure}[H]
+    \centering
+    \frame{\includegraphics[scale=1.15]{figures/Barplot_Estatisticas_por_Algoritmo_Prob_0_05.png}}
+    \textsf{\caption[Data for \textit{probability of failure} of 5\%.]{Data for \textit{probability of failure} of 5\%.\label{fig-barplot-pof-005}}}
+\end{figure}
+
+Considering the data in the graphs, we can conclude that Bubblesort generates lower mean value for variable \%UEQ for all defined combinations (\textit{probability of failure} X \textit{array size} X \textit{sorting algorithm}).
+These data demonstrate that Bubblesort was the less affected algorithm by the memory faults simulated in this experiment.
+We believe that this fact happens because of the operation of the algorithm itself, where all elements order are verified each iteration, causing an element incorrectly positioned in an iteration (because of a memory fault) can have its location corrected in an upcoming iteration.
+
+Related to Bubblesort yet, we could identify that despite different sizes of input arrays (100, 1000, and 10000), there wasn't a significant impact on the mean value obtained for \%UEQ variable, proving what we verify with ANOVA when doing hypothesis 3 testing for this algorithm.

### 2019-12-22 paper/ExperimentalSetup.tex
finalização da escrita do artigo

@@
 
-We first state our problem, then describe our data, showing all its characteristics.
-Then, we provide our hypothesis, define the setup, and perform the testing.
-Finally, we collect and perform data analysis.
+In this section, we present the setup of this study.
+We first state our problem, then define the independent and dependent variables.
+After that, we show the hypothesis and describe our dataset, showing all its characteristics.
 
@@
 
-% \setcounter{hyp}{-1}
-% \begin{hyp}[Test hypothesis] \label{hyp:a}There is no difference in memory faults between tested algorithms.\end{hyp}
-% \begin{hyp} \label{hyp:b}There are differences in memory faults between tested algorithms. \end{hyp}
-% \begin{hyp} \label{hyp:c} An algorithm is better than others considering all dependent variables. \end{hyp}
-
-% \begin{hyp} \label{hyp:d} ... \end{hyp}
-
 \subsection{Dataset}
@@
 Figure \ref{fig-input-file-example} shows an example of produced input files:
-
-% \begin{itemize}
-%     \item A script that generates input files;
-%     \item Four files, one for each of those algorithms: quicksort, bubblesort, insertion sort, and mergesort, that are used to sorting the input data;
-% \end{itemize}
 
@@
 An output file look like shown in Figure \ref{fig-output-file-example}:
-
-% We run 1000 times each algorithm with each file listed in Table \ref{table-input-data} below.
-We chose this number of executions to reduce possible noise in the generated data.
-Table \ref{table-input-data} shows 9 different input files with its sequence sizes and probabilities of failure.
-Plus, the number of executions and each sorting algorithm.
-
-% For example, Input A showed in that table with its characteristics was executed 1000 times for each algorithm -  bubblesort, quicksort, mergesort, and insertion sort - totalizing 4000 executions.
-
-% \begin{table}[H]
-%     \caption{Generated input data.}
-%     \begin{center}
-%     \begin{tabular}{|c|c|c|c|c|}
-%     \hline
-%     \textbf{Input} & \textbf{Sequence Size} & \textbf{Probability of Failure} & \textbf{Executions} & \textbf{Algorithm} \\ 
-%     \hline
-%     \multirow{4}{*}{Input A} & \multirow{4}{*}{100} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input B} & \multirow{4}{*}{100} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input C} & \multirow{4}{*}{100} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input D} & \multirow{4}{*}{1000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input E} & \multirow{4}{*}{1000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input F} & \multirow{4}{*}{1000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input G} & \multirow{4}{*}{10000} & \multirow{4}{*}{1\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input H} & \multirow{4}{*}{10000} & \multirow{4}{*}{2\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \multirow{4}{*}{Input I} & \multirow{4}{*}{10000} & \multirow{4}{*}{5\%} & \multirow{4}{*}{1000} & Bubblesort \\ 
-%     & & & & Quicksort \\
-%     & & & & Mergesort \\
-%     & & & & Insertion Sort \\
-%     \hline
-%     \end{tabular}
-%     \label{table-input-data}
-%     \end{center}
-% \end{table}
-
-% Each execution generates an output file.
-Then, we generate 4000 outputs for each combination of sequence size, and the probability of failure, totalizing 36000 files.
-Figure \ref{fig-output-file-example} shows an output file.
 
@@
 
-After generating the dataset, we developed a Python script that reads the 1080 output files and produces a single CSV file (first lines showed in Figure \ref{fig-output-csv-file-example} below), containing the following columns:
+After generating the dataset, we developed a Python script that reads the 1080 output files and produces a single CSV file (first lines showed in Figure \ref{fig-output-csv-file-example} below).
+This file was used to run the statistical tests, and contains the following columns:
 \begin{itemize}
@@
 \end{itemize}
-
-% \subsection{Data Analysis}
-
-% In this section, we describe our data and the statistic tests used to test the hypothesis showed before.
-
-% \subsubsection{Exploratory Data Analysis (EDA)}
-
-% Based on the output files generated before, our starting point was to test if the dataset had a normal distribution.
-To achieve this, we use Shapiro-Wilk normality test.
-After we run these tests, only the distribution related to the dependent variable \textit{unordered elements size} was considered normal.
-Figure \ref{fig-distribution-graph} shows an example of this distribution.
-In these graphs, the red vertical line means the mean, and the blue vertical line means the median.
-The distributions were normal in all combinations of independent variables for dependent variable \textit{unordered elements size}.
-
-% \begin{figure}[H]
-%     \centering
-%      \begin{subfigure}{.5\textwidth}
-%      \centering
-%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Bubble_distribution_graph}}
-%      \textsf{\caption[Distribution Graph for bubblesort.]{Distribution Graph for bubblesort.\label{fig-dist-bubble-001-100}}}
-%      \end{subfigure}%
-%      \begin{subfigure}{.5\textwidth}
-%      \centering
-%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Insertion_distribution_graph.png}}
-%      \textsf{\caption[Distribution Graph for insertion sort.]{Distribution Graph for insertion sort.\label{fig-dist-insertion-001-100}}}
-%      \end{subfigure}
-%      \begin{subfigure}{.5\textwidth}
-%      \centering
-%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Merge_distribution_graph.png}}
-%      \textsf{\caption[Distribution Graph for mergesort.]{Distribution Graph for mergesort.\label{fig-dist-merge-001-100}}}
-%      \end{subfigure}%
-%      \begin{subfigure}{.5\textwidth}
-%      \centering
-%      \frame{\includegraphics[scale=0.12]{figures/0_01_10000_Quick_distribution_graph.png}}
-%      \textsf{\caption[Distribution Graph for quicksort.]{Distribution Graph for quicksort.\label{fig-dist-quick-001-100}}}
-%      \end{subfigure}
-%      \caption{Distribution graph for a probability failure of 1\% and a sequence size of 10000.}
-%     \label{fig-distribution-graph}
-% \end{figure}
-
-% Q-Q plot shows that how much more blue points close to the red line, most normal is the distribution.
-Figure \ref{fig-qqplot} below presents this graph for a probability failure of 1\% and a sequence size of 10000 for considered sorting algorithms.
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.37]{figures/anova_prob_0_01_tam_10000_DESORDENADOS_PERCENTUAL.png}
-%     \textsf{\caption[Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.]{Q-Q plot showing normal distribution for a probability failure of 1\% and a sequence size of 10000.\label{fig-qqplot}}}
-%  \end{figure}
-
-\subsection{Conclusions}

### 2019-12-22 paper/article.tex
finalização da escrita do artigo

--- 2019-12-21 paper/article.tex
@@
 
-\input{Results}
-
-\input{Discussion}
-
 \input{Conclusion}
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
 

### 2019-12-23 paper/DataAnalysis.tex
Revisao 01 do paper

@@
 In this section, we present our results after the execution of sorting algorithms over the input files.
-We analyzed only the dependent variables \textit{percentage of the largest subarray size ((\%LSS)} and \textit{percentage of unordered elements quantity (\%UEQ)}.
+We analyzed only two of the four dependent variables, which were \textit{percentage of the largest subarray size (\%LSS)} and \textit{percentage of unordered elements quantity (\%UEQ)}.
 These variables, because they are a percentage value, already were normalized (i.e., the same order of magnitude) related to dependent variable \textit{array size}.
@@
 After the Shapiro-Wilk test, we determine that only the dependent variable \%UEQ (\textit{percentage of unordered elements quantity}) has a normal distribution related to mean for all algorithms.
-This situation occurs considering all possible combinations between independent variables: \textit{sorting algorithm}, \textit{probability of failure} and \textit{array size}.
+This situation occurred considering all possible combinations between independent variables: \textit{sorting algorithm}, \textit{probability of failure} and \textit{array size}.
 
 Based on these results, we choose to test just the hypothesis associated with the dependent variable \%UEQ.
-We make use of the ANOVA method to test the hypothesis, and this method is premised the normal distribution of variables values.
+We made use of the ANOVA method to test the hypothesis, and this method is premised the normal distribution of variables values.
 
@@
         \hline
-        Bubblesort & 0.891642 & 0.00052 \\
+        Bubblesort & 0.891642 & 0.0052 \\
         \hline
-        Insertion Sort & 0.921918 & 0.3000 \\
+        Insertion Sort & 0.921918 & 0.0300 \\
         \hline
@@
     \hline
-    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Insertion sort}} \\
+    \multirow{2}{*}{\hfill}&\multicolumn{4}{|c|}{\textbf{Insertionsort}} \\
     \cline{2-5}
@@
 Analyzing the result, we can affirm with 95\% of confidence that the value of \textit{probability of failure} variable had a significant impact on the value of the dependent variable \%UEQ.
-But we can't affirm the same related to independent variable \textit{array size}.
-These results demonstrate that, for Bubblesort algorithm, the array sizes used in this experiment were not decisive to define values concerning the percentage of unordered elements quantity.
+But we can not affirm the same related to independent variable \textit{array size}.
+These results demonstrate that, for the Bubblesort algorithm, the array sizes used in this experiment were not decisive to define values concerning the percentage of unordered elements quantity.
 
@@
 To help this analysis, we show below 3 bar graphs, each of these for a different value of \textit{probability of failure} independent variable.
-These graphs shows informations about values of \%UEQ variable grouped by \textit{array size} and \textit{sorting algorithm} variables.
+These graphs show information about values of \%UEQ variable grouped by \textit{array size} and \textit{sorting algorithm} variables.
 Figures \ref{fig-barplot-pof-001}, \ref{fig-barplot-pof-002}, and \ref{fig-barplot-pof-005} below exhibit these graphs.
 
-The bars in each graph represents the sample mean value for variable \%UEQ inside each group.
+The bars in each graph represent the sample mean value for variable \%UEQ inside each group.
 Above each bar, there is a vertical line that indicates the lower and upper limits of a confidence interval for a significance level of 5\% ($\alpha = 0.05$).
@@
 These data demonstrate that Bubblesort was the less affected algorithm by the memory faults simulated in this experiment.
-We believe that this fact happens because of the operation of the algorithm itself, where all elements order are verified each iteration, causing an element incorrectly positioned in an iteration (because of a memory fault) can have its location corrected in an upcoming iteration.
+We believe that this fact happened because of the operation of the algorithm itself, where all elements order are verified each iteration, causing an element incorrectly positioned in an iteration (because of a memory fault) can have its location corrected in an upcoming iteration.
 
-Related to Bubblesort yet, we could identify that despite different sizes of input arrays (100, 1000, and 10000), there wasn't a significant impact on the mean value obtained for \%UEQ variable, proving what we verify with ANOVA when doing hypothesis 3 testing for this algorithm.
+Related to Bubblesort yet, we could identify that despite different sizes of input arrays (100, 1000, and 10000), there was not a significant impact on the mean value obtained for \%UEQ variable, proving what we verify with ANOVA when doing hypothesis 3 testing for this algorithm.

### 2019-12-23 paper/ExperimentalSetup.tex
Revisao 01 do paper

@@
     \hline
-    Sorting algorithm & Bubblesort, Quicksort, Mergesort and Insertion sort \\
+    Sorting algorithm & Bubblesort, Quicksort, Mergesort and Insertionsort \\
     \hline
@@
     \item \textit{Sequence size}: the second number (\texttt{100}) means the size of the integers sequence used by sorting;
-    \item \textit{Sequence}: the rest of the numbers indicates the sequence itself.
+    \item \textit{Sequence}: the rest of the numbers represents a list of \textit{n} positive integers that will be sorted.
 \end{itemize}
@@
 At the end of executions, we get a total of 1080 output files.
-An output file look like shown in Figure \ref{fig-output-file-example}:
+An output file looks like shown in Figure \ref{fig-output-file-example}:
 
@@
 \begin{itemize}
-    \item \textit{[1]}: the original sequence of integers contained in the input file;
-    \item \textit{[2]}: the sequence processed by the sorting algorithm under the memory fault model;
-    \item \textit{[3]}: the sequence sorted correctlty;
-    \item \textit{[4]}: the size of the largest sorted subsequence in [2]. This number can be interpreted as the quality of sorting. As higher, most successful was the sorting operation.
+    \item \textit{1)} the original sequence of integers contained in the input file;
+    \item \textit{2)} the sequence processed by the sorting algorithm under the memory fault model;
+    \item \textit{3)} the sequence sorted correctly;
+    \item \textit{4)} the size of the largest sorted subsequence in item \textit{2}. This number can be interpreted as a quality measure. As higher, most successful was the sorting operation.
 \end{itemize}
 
-After generating the dataset, we developed a Python script that reads the 1080 output files and produces a single CSV file (first lines showed in Figure \ref{fig-output-csv-file-example} below).
-This file was used to run the statistical tests, and contains the following columns:
+After generating the dataset, we developed a Python program that reads the 1080 output files and produces a single CSV file (first lines showed in Figure \ref{fig-output-csv-file-example}).
+This file contains the columns listed below and was used to perform the exploratory data analysis and to run the statistical tests.
 \begin{itemize}
-    \item \textit{algorithm}: the algorithm used to sort the array;
+    \item \textit{sorting\_algorithm}: the algorithm used to sort the array;
     \item \textit{probability\_of\_failure}: the probability of failure used when sorting;
-    \item \textit{size\_of\_array}: the size of the array to be sorted;
-    \item \textit{largest\_sorted\_subarray}: the largest sorted subarray after sorting;
-    \item \textit{k\_unordered\_sequence}: number of unordered sequence after sorting.
-    \item \textit{percentage\_k\_unordered}: percentage of unordered sequence after sorting related to original array;
-    \item \textit{percentage\_largest\_sorted\_subarray}: percentage of largest sorted subarray after sorting related to original array.
+    \item \textit{array\_size}: the size of the sorted array;
+    \item \textit{largest\_subarray\_size}: the largest sorted subarray after sorting;
+    \item \textit{unordered\_elements\_quantity}: quantity of unordered sequence elements after sorting.
+    \item \textit{perc\_unordered\_elements\_quantity}: percentage of unordered elements after sorting related to original array;
+    \item \textit{perc\_largest\_subarray\_size}: percentage of largest sorted subarray after sorting related to original array.
 \end{itemize}
@@
 \begin{verbbox}[\mbox{}]
-algorithm;probability_of_failure;size_of_array;largest_sorted_subarray;
-k_unordered_sequence;percentage_k_unordered;
-percentage_largest_sorted_subarray
+sorting_algorithm;probability_of_failure;array_size;largest_subarray_size;
+unordered_elements_quantity;perc_unordered_elements_quantity;
+perc_largest_subarray_size
 quick;0.01;100;35;4;4.00;35.00

### 2019-12-23 paper/ExperimentalSetup.tex
alteração na numeração da linha na pagina 5

@@
 \begin{verbbox}[\mbox{}]
-[1]  9 48 37 6 26 7 24 44 17 50 48 30 49 33 22 13 42 29 39 13 19 13 9 28 34 1
+#1  9 48 37 6 26 7 24 44 17 50 48 30 49 33 22 13 42 29 39 13 19 13 9 28 34 1
 33 27 14 45 48 40 11 17 6 50 9 44 20 16 37 45 23 14 38 29 10 49 44 46 35 45  
@@
 1 11 44 26 50 44 12 7 20 30 20 37 20 6 8 13 15 20 49
-[2]  1 1 1 2 3 4 5 6 6 6 6 7 7 8 8 8 9 9 9 9 10 11 11 12 13 13 13 13 14 14 15 
+#2  1 1 1 2 3 4 5 6 6 6 6 7 7 8 8 8 9 9 9 9 10 11 11 12 13 13 13 13 14 14 15 
 15 15 16 17 17 17 19 20 20 20 20 22 22 23 23 23 24 24 25 26 26 27 27 28 28 28 
@@
 45 45 45 46 46 48 48 48 48 48 49 49 50 49 50 50 50
-[3]  1 1 1 2 3 4 5 6 6 6 6 7 7 8 8 8 9 9 9 9 10 11 11 12 13 13 13 13 14 14 15 
+#3  1 1 1 2 3 4 5 6 6 6 6 7 7 8 8 8 9 9 9 9 10 11 11 12 13 13 13 13 14 14 15 
 15 15 16 17 17 17 19 20 20 20 20 20 22 22 23 23 23 24 24 25 26 26 27 27 28 28 
@@
 45 45 45 46 46 48 48 48 48 48 49 49 49 50 50 50 50
-[4]  82
+#4  82
 \end{verbbox}
@@
 \begin{itemize}
-    \item \textit{1)} the original sequence of integers contained in the input file;
-    \item \textit{2)} the sequence processed by the sorting algorithm under the memory fault model;
-    \item \textit{3)} the sequence sorted correctly;
-    \item \textit{4)} the size of the largest sorted subsequence in item \textit{2}. This number can be interpreted as a quality measure. As higher, most successful was the sorting operation.
+    \item \textit{\#1}: the original sequence of integers contained in the input file;
+    \item \textit{\#2}: the sequence processed by the sorting algorithm under the memory fault model;
+    \item \textit{\#3}: the sequence sorted correctly;
+    \item \textit{\#4}: the size of the largest sorted subsequence in item \textit{2}. This number can be interpreted as a quality measure. As higher, most successful was the sorting operation.
 \end{itemize}

### 2020-02-06 paper/Conclusion.tex
alteracao no artigo.
Inclusão da regressão linear e alterações sugeridas pelo professor.

@@
 
+For linear regression, our results showed that for dependent variable \%UEQ variable we get a linear model that explains at least 80\% of relation between this variable and indepentent variable probability of failure.
+
 We can, then, with our results, elaborate a ranking of the performance of algorithms when considering memory faults:
@@
 \end{enumerate}
+
+All data used for this work can be downloaded at \href{https://bit.ly/392LZKR}{https://bit.ly/392LZKR}.

### 2020-02-06 paper/DataAnalysis.tex
Inclusão da regressão linear e alterações sugeridas pelo professor.

@@
 
-The following Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000} illustrates examples of histograms and boxplot graphs for each combination of \textit{Algorithm X Probability of Failure X Array Size}.
+The following Figures \ref{fig-histogram-lss-001-100}, \ref{fig-histogram-ueq-001-100} and \ref{fig-boxplots-001-100} illustrates examples of histograms and boxplot graphs for each combination of \textit{Algorithm X Probability of Failure X Array Size}.
 In each of those figures, the graphs were exhibited over the dependent variables \%LSS and \%UEQ.
-In the histogram, the red vertical line means the mean, and the blue vertical line means the median.
-On the other hand, in the boxplot, the red horizontal line means the mean, and the blue horizontal line means the median.
 
@@
     \centering
-    \frame{\includegraphics[scale=0.105]{figures/0_01_100_Bubble.png}}
-    \caption{Histograms and Boxplot for Bubblesort, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
-    \label{fig-histogram-boxplot-bubble-001100}
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_bubble_LSS_001_100.png}}
+     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-bubble-lss-001-100}}}
+     \end{subfigure}%
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_insertion_LSS_001_100.png}}
+     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-insertion-lss-001-100}}}
+     \end{subfigure}
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_merge_LSS_001_100.png}}
+     \textsf{\caption[Histogram for Mergesort.]{Histogram for Mergesort.\label{fig-histogram-mergesort-lss-001-100}}}
+     \end{subfigure}%
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_quick_LSS_001_100.png}}
+     \textsf{\caption[Histogram for Quicksort.]{Histogram for Quicksort.\label{fig-histogram-quicksort-lss-001-100}}}
+     \end{subfigure}
+     \caption{Histograms for \%LSS, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
+    \label{fig-histogram-lss-001-100}
   \end{figure}
 
-Based on Figures \ref{fig-histogram-boxplot-bubble-001100}, \ref{fig-histogram-boxplot-insertion-001100}, \ref{fig-histogram-boxplot-merge-00510000} and \ref{fig-histogram-boxplot-quick-00510000}, the following Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss} illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.
+Based on Figures \ref{fig-histogram-lss-001-100}, \ref{fig-histogram-ueq-001-100} and \ref{fig-boxplots-001-100}, the following Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss} illustrates the information about the dependent variables (\%LSS and \%UEQ) distribution.
 
 \begin{table}[H]
-    \caption{Table Type Styles}
+    \caption{Dependent variable \%UEQ distribution.}
     \begin{center}
@@
     \centering
-    \frame{\includegraphics[scale=0.105]{figures/0_01_100_Insertion.png}}
-    \caption{Histograms and Boxplot for Insertion sort, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
-    \label{fig-histogram-boxplot-insertion-001100}
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_bubble_UEQ_001_100.png}}
+     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-bubble-ueq-001-100}}}
+     \end{subfigure}%
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_insertion_UEQ_001_100.png}}
+     \textsf{\caption[Histogram for Bubblesort.]{Histogram for Bubblesort.\label{fig-histogram-insertion-ueq-001-100}}}
+     \end{subfigure}
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_merge_UEQ_001_100.png}}
+     \textsf{\caption[Histogram for Mergesort.]{Histogram for Mergesort.\label{fig-histogram-mergesort-ueq-001-100}}}
+     \end{subfigure}%
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/histogram_quick_UEQ_001_100.png}}
+     \textsf{\caption[Histogram for Quicksort.]{Histogram for Quicksort.\label{fig-histogram-quicksort-ueq-001-100}}}
+     \end{subfigure}
+     \caption{Histograms for \%UEQ, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
+    \label{fig-histogram-ueq-001-100}
   \end{figure}
@@
 \begin{table}[H]
-    \caption{Table Type Styles}
+    \caption{Dependent variable \%LSS distribution.}
     \begin{center}
@@
 
-\begin{figure}[H]
-    \centering
-    \frame{\includegraphics[scale=0.105]{figures/0_05_10000_Merge.png}}
-    \caption{Histograms and Boxplot for Mergesort, with \textit{probability of failure} of 0.05 and \textit{array size} of 10000.}
-    \label{fig-histogram-boxplot-merge-00510000}
-\end{figure}
+We produced graphs with the same data showed in Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss}.
+Figure \ref{fig-distribution-all-algorithms-001-all-sizes} shows an example of these graphs.
+On it, we illustrate on the top-left graph that, considering the mean, bubblesort produces fewer unordered elements related to the total than other algorithms.
 
@@
     \centering
-    \frame{\includegraphics[scale=0.105]{figures/0_05_10000_Quick.png}}
-    \caption{Histograms and Boxplot for Quicksort, with \textit{probability of failure} of 0.05 and \textit{array size} of 10000.}
-    \label{fig-histogram-boxplot-quick-00510000}
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/boxplot_lss_001_100.png}}
+     \textsf{\caption[Boxplot for \%LSS.]{Boxplot for \%LSS.\label{fig-boxplot-lss-001-100}}}
+     \end{subfigure}%
+     \begin{subfigure}{.5\textwidth}
+     \centering
+     \frame{\includegraphics[scale=0.45]{figures/boxplot_ueq_001_100.png}}
+     \textsf{\caption[Boxplot for \%UEQ.]{Boxplot for \%UEQ.\label{fig-boxplot-ueq-001-100}}}
+     \end{subfigure}
+     \caption{Boxplots for \%LSS and \%UEQ variables, with \textit{probability of failure} of 0.01 and \textit{array size} of 100.}
+    \label{fig-boxplots-001-100}
 \end{figure}
-
-We produced graphs with the same data showed in Tables \ref{tab-distribution-depentent-variable-ueq} and \ref{tab-distribution-depentent-variable-lss}.
-Figure \ref{fig-distribution-all-algorithms-001-all-sizes} shows an example of these graphs.
-On it, we illustrate on the top-left graph that, considering the mean, bubblesort produces fewer unordered elements related to the total than other algorithms.
 
@@
     \hline
-    size\_of\_array & 0.019548 & 1.0 & 0.01350 & \textbf{0.90759} \\
+    size\_of\_array & 0.019548 & 2.0 & 0.01350 & \textbf{0.90759} \\
     \hline
-    probability\_of\_failure & 3590.644437 & 1.0 & 2479.71637 & \textbf{7.570027e-137} \\
+    probability\_of\_failure & 3590.644437 & 2.0 & 2479.71637 & \textbf{7.570027e-137} \\
     \hline
@@
     \hline
-    size\_of\_array & 1784.873256 & 1.0 & 383.585800 & \textbf{1.702008e-53} \\
+    size\_of\_array & 1784.873256 & 2.0 & 383.585800 & \textbf{1.702008e-53} \\
     \hline
-    probability\_of\_failure & 13009.963175 & 1.0 & 2795.961630 & \textbf{3.801570e-143} \\
+    probability\_of\_failure & 13009.963175 & 2.0 & 2795.961630 & \textbf{3.801570e-143} \\
     \hline
@@
     \hline
-    size\_of\_array & 121.551362 & 1.0 & 32.964196 & \textbf{2.556033e-08} \\
+    size\_of\_array & 121.551362 & 2.0 & 32.964196 & \textbf{2.556033e-08} \\
     \hline
-    probability\_of\_failure & 5626.955128 & 1.0 & 1526.005558 & \textbf{3.457996e-112} \\
+    probability\_of\_failure & 5626.955128 & 2.0 & 1526.005558 & \textbf{3.457996e-112} \\
     \hline
@@
     \hline
-    size\_of\_array & 309.843991 & 1.0 & 75.905868 & \textbf{3.236586e-16} \\
+    size\_of\_array & 309.843991 & 2.0 & 75.905868 & \textbf{3.236586e-16} \\
     \hline
-    probability\_of\_failure & 6806.075083 & 1.0 & 1667.358570 & \textbf{1.414758e-116} \\
+    probability\_of\_failure & 6806.075083 & 2.0 & 1667.358570 & \textbf{1.414758e-116} \\
     \hline

### 2020-02-06 paper/LinearRegression.tex
Inclusão da regressão linear e alterações sugeridas pelo professor.

\section{Linear Regression}

The linear regression analysis consists of statistical analysis to verify the existence of a functional relationship between a dependent variable with one or more independent variables. In other words, this analysis consists of obtaining a linear equation that tries to explain the variation from the dependent variable by variation from the independent variable level.

The statistical model for this case should be:
\begin{equation} 
    \label{eqn_example}
    y = a.x + b
\end{equation}

Where $y$ represents the dependent variable, $a$ represents the line slope of the linear model, and $b$ represents the y-axis intercept. The regression line is a method to calculate the parameters $a$ and $b$.

The determination coefficient, frequently called $R^2$, or simply $r^2$, for the linear regression case, provide auxiliary information to the analysis of the result of regression variance, as a way to verify if the proposed model is suitable or not to describe the phenomenon.

In this work, we verified how close is the relationship between the \textit{probability of failure} independent variable and the other dependent variables: \%LSS and \%UEQ to a linear equation.

To discover an equation that represents the studied phenomenon, we could build a graph, called \textit{Scatter Plot}, to verify by visualization how is the variation between the dependent and independent variables.

To discover an equation that represents the studied phenomenon, we could build a graph, called scatter plot, to verify by visualization how is the variation between the dependent and independent variables. Figures \ref{fig-linear-regression-scatter-plots-lss} and \ref{fig-linear-regression-scatter-plots-ueq} are the scatter plots for \%LSS and \%UEQ for each algorithm, respectively. In these figures, we can see the line from the linear equation from the estimated model that used the minimum mean square error as criteria. The red dotted line represents the bounds for 95\% of the confidence interval.

\begin{figure}[H]
    \centering
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_lss_bubble.png}}
     \textsf{\caption[Bubblesort algorithm.]{Bubblesort algorithm.\label{fig-linear-regression-scatter-plot-lss-bubble}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_lss_insertion.png}}
     \textsf{\caption[Insertionsort algorithm.]{Insertionsort algorithm.\label{fig-linear-regression-scatter-plot-lss-insertion}}}
     \end{subfigure}
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_lss_merge.png}}
     \textsf{\caption[Mergesort algorithm.]{Mergesort algorithm.\label{fig-linear-regression-scatter-plot-lss-merge}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_lss_quick.png}}
     \textsf{\caption[Quicksort algorithm.]{Quicksort algorithm.\label{fig-linear-regression-scatter-plot-lss-quick}}}
     \end{subfigure}
     \caption{Scatter plot and the linear regression for \%LSS versus Probability of Failure.}
    \label{fig-linear-regression-scatter-plots-lss}
  \end{figure}

  \begin{figure}[H]
    \centering
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_ueq_bubble.png}}
     \textsf{\caption[Bubblesort algorithm.]{Bubblesort algorithm.\label{fig-linear-regression-scatter-plot-ueq-bubble}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_ueq_insertion.png}}
     \textsf{\caption[Insertionsort algorithm.]{Insertionsort algorithm.\label{fig-linear-regression-scatter-plot-ueq-insertion}}}
     \end{subfigure}
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_ueq_merge.png}}
     \textsf{\caption[Mergesort algorithm.]{Mergesort algorithm.\label{fig-linear-regression-scatter-plot-ueq-merge}}}
     \end{subfigure}%
     \begin{subfigure}{.5\textwidth}
     \centering
     \frame{\includegraphics[scale=0.45]{figures/linear_regression_scatter_plot_ueq_quick.png}}
     \textsf{\caption[Quicksort algorithm.]{Quicksort algorithm.\label{fig-linear-regression-scatter-plot-ueq-quick}}}
     \end{subfigure}
     \caption{Scatter plot and the linear regression for \%UEQ versus Probability of Failure.}
    \label{fig-linear-regression-scatter-plots-ueq}
  \end{figure}

  However, we can verify that the points at scatter plots, don't have perfect adjust to the proposed math model line. There are, in major part, a great distance between the points at the plot and the model line. This distance happens because, in each probability of failure, we have many values of the dependent variable and with large dispersion. This situation explains why the determination coefficient $r^2$ has a low value in most of the cases.

  The Tables \ref{table-linear-regression-lss} and \ref{table-linear-regression-ueq} below shows the parameters for linear regression of both variables \%LSS and \%UEQ. For \%UEQ variable, we found better (from 0.809 to 0.899) $r^2$ than \%LSS (from 0.0499 to 0.141) variable for all algorithms.

  \begin{table}[H]
    \caption{Parameters from linear regression for the \%LSS variable.}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \textbf{Parameter} & \textbf{Bubblesort} & \textbf{Quicksort} & \textbf{Mergesort} & \textbf{Insertionsort} \\
    \hline
    Intercept (b) & 36.576 & 14.86 & 20.651 & 8.5707 \\
    \hline
    Slope (a) & -512.32 & -176.4 & -333.64 & -90.711 \\
    \hline
    $r^2$ & 0.141 & 0.0499 & 0.101 & 0.0399 \\
    \hline
    Root Mean Squared Error (RMSE) & 21.5 & 13.1 & 17 & 7.59 \\
    \hline
    \end{tabular}
    \label{table-linear-regression-lss}
    \end{center}
\end{table}

\begin{table}[H]
    \caption{Parameters from linear regression for the \%UEQ variable.}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \textbf{Parameter} & \textbf{Bubblesort} & \textbf{Quicksort} & \textbf{Mergesort} & \textbf{Insertionsort} \\
    \hline
    Intercept (b) & 1.4429 & 4.3258 & 4.1165 & 10.426 \\
    \hline
    Slope (a) & -214.56 & 268.59 & 408.4 & 295.39 \\
    \hline
    $r^2$ & 0.899 & 0.823 & 0.809 & 0.826 \\
    \hline
    Root Mean Squared Error (RMSE) & 1.23 & 2.12 & 3.38 & 2.31 \\
    \hline
    \end{tabular}
    \label{table-linear-regression-ueq}
    \end{center}
\end{table}
